---
title: "Study 1 analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 150, cache = FALSE)
options(scipen = 999)
set.seed(65)
```

In this report, we reproduce the exploratory Study 1 analyses examining downstream effects of the interventions.

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, kableExtra, lmerTest, boot, report, brms, tidybayes, ggpubr, tidyText, EMAtools, broom.mixed, devtools, emmeans)

if (!require(emo)) {
  devtools::install_github('hadley/emo')
}
```

## define functions
```{r}
# MLM results table function
table_model = function(model_data, eff_size = FALSE, logistic = FALSE, lm = FALSE) {

  if (lm == TRUE) {
    results = model_data %>%
      broom::tidy(conf.int = TRUE) %>%
      rename("SE" = std.error,
             "t" = statistic,
             "p" = p.value) %>%
      mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type", term),
             term = gsub("msg_share_narrow", " (narrow)", term),
             term = gsub("msg_rel_self_between", "self-relevance between", term),
             term = gsub("msg_rel_social_between", "social relevance between", term),
             term = gsub("msg_rel_self_within", "self-relevance within", term),
             term = gsub("msg_rel_social_within", "social relevance within", term),
             term = gsub("action_current", "current behavior", term),
             term = gsub("n_c", "word count", term),
             term = gsub("self$", "self - control", term),
             term = gsub("other$", "other - control", term),
             term = gsub(":", " x ", term),
             p = ifelse(p < .001, "< .001",
                        ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
             `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) 
    
  } else {
    results = model_data %>%
      broom.mixed::tidy(conf.int = TRUE) %>%
      filter(effect == "fixed") %>%
      rename("SE" = std.error,
             "t" = statistic,
             "p" = p.value) %>%
      select(-group, -effect) %>%
      mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type", term),
             term = gsub("msg_share_narrow", " (narrow)", term),
             term = gsub("msg_rel_self_between", "self-relevance between", term),
             term = gsub("msg_rel_social_between", "social relevance between", term),
             term = gsub("msg_rel_self_within", "self-relevance within", term),
             term = gsub("msg_rel_social_within", "social relevance within", term),
             term = gsub("action_current", "current behavior", term),
             term = gsub("n_c", "word count", term),
             term = gsub("self$", "self - control", term),
             term = gsub("other$", "other - control", term),
             term = gsub(":", " x ", term),
             p = ifelse(p < .001, "< .001",
                        ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
             `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) 
  }
  
  if (eff_size == TRUE) {
    
    eff_size = effectsize::effectsize(model_data, type = "d") %>%
      data.frame() %>%
      rename("term" = Parameter) %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type", term),
             term = gsub("msg_rel_self_between", "self-relevance between", term),
             term = gsub("msg_rel_social_between", "social relevance between", term),
             term = gsub("msg_rel_self_within", "self-relevance within", term),
             term = gsub("msg_rel_social_within", "social relevance within", term),
             `d [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", Std_Coefficient, CI_low, CI_high)) %>%
      select(term, `d [95% CI]`)
    
    if (lm == TRUE) {
      
      results %>%
        left_join(., eff_size) %>%
        select(term, `b [95% CI]`, `d [95% CI]`, t, p) %>%
        kable() %>%
        kableExtra::kable_styling()
      
    } else {
      
      results %>%
        left_join(., eff_size) %>%
        select(term, `b [95% CI]`, `d [95% CI]`, df, t, p) %>%
        kable() %>%
        kableExtra::kable_styling()
      
    }
    
  } else if (logistic == TRUE | lm == TRUE) {
    results %>%
      select(term, `b [95% CI]`, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
    
  } else {
    results %>%
      select(term, `b [95% CI]`, df, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
  }
}

# Run bayesian mediation model
run_brm_model = function(model_name, model_formula, y_var, data) {
  if (file.exists(sprintf("models/model_%s.RDS", model_name))) {
    assign(get("model_name"), readRDS(sprintf("models/model_%s.RDS", model_name)))
  } else {
    
    assign(get("model_name"),
           brm(
             model_formula,
             data = data,
             cores = 4,
             thin = 4,
             seed = seed,
             control = list(adapt_delta = .99, max_treedepth = 15)
        ))
    
    saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s.RDS", model_name))
    return(eval(parse(text = model_name)))
  }
}

# Get path estimates from bayesian mediation models
create_paths = function(model, x_var, y_var) {
  paths = posterior_samples(model) %>% 
    mutate(a1 = get(sprintf("b_msgrelself_article_cond%s", x_var)),
           a2 = get(sprintf("b_msgrelsocial_article_cond%s", x_var)),
           b1 = get(sprintf("b_%s_msg_rel_self", y_var)),
           b2 = get(sprintf("b_%s_msg_rel_social", y_var)),
           c_prime = get(sprintf("b_%s_article_cond%s", y_var, x_var)),
           a1b1 = a1 * b1,
           a2b2 = a2 * b2,
           c = c_prime + a1b1 + a2b2,
           cor1 = get(sprintf("cor_SID__msgrelself_Intercept__%s_msg_rel_self", y_var)),
           cor2 = get(sprintf("cor_SID__msgrelsocial_Intercept__%s_msg_rel_social", y_var)),
           sd_a1 = sd_SID__msgrelself_Intercept,
           sd_b1 = get(sprintf("sd_SID__%s_msg_rel_self", y_var)),
           sd_a2 = sd_SID__msgrelsocial_Intercept,
           sd_b2 = get(sprintf("sd_SID__%s_msg_rel_social", y_var)),
           cov_a1b1 = cor1*sd_a1*sd_b1,
           cov_a2b2 = cor2*sd_a2*sd_b2,
           a1b1_cov_a1b1 = a1b1 + cov_a1b1,
           a2b2_cov_a2b2 = a2b2 + cov_a2b2,
           model = x_var,
           outcome = y_var)
  
  return(paths)
}

create_paths_words = function(model, x_var, y_var) {
  y_var = gsub("_", "", y_var)
  paths = posterior_samples(model) %>% 
    mutate(a1 = get(sprintf("b_nc_article_cond%s", x_var)),
           b1 = get(sprintf("b_%s_n_c", y_var)),
           c_prime = get(sprintf("b_%s_article_cond%s", y_var, x_var)),
           a1b1 = a1 * b1,
           c = c_prime + a1b1,
           cor1 = get(sprintf("cor_SID__nc_article_cond%s__%s_n_c", x_var, y_var)),
           sd_a1 = get(sprintf("sd_SID__nc_article_cond%s", x_var)),
           sd_b1 = get(sprintf("sd_SID__%s_n_c", y_var)),
           cov_a1b1 = cor1*sd_a1*sd_b1,
           a1b1_cov_a1b1 = a1b1 + cov_a1b1,
           model = x_var,
           outcome = y_var)
  
  return(paths)
}

get_paths = function(model, x_var, y_var) {
  create_paths(model, x_var, y_var) %>% 
    select(a1:a2b2_cov_a2b2, -contains("sd"), -contains("cor"), -starts_with("cov")) %>% 
    gather(path, value) %>% 
    article_cond_by(path) %>% 
    summarize(median = median(value),
              `Mdn [95% CI]` = sprintf("%.2f [%.2f, %.2f]", median(value), quantile(value, probs = .025), quantile(value, probs = .975))) %>%
    mutate(path = factor(path, levels = c("a1", "b1", "a1b1", "a1b1_cov_a1b1", "a2", "b2", "a2b2", "a2b2_cov_a2b2", "c", "c_prime")),
           variable = ifelse(grepl("1", path), "self-relevance",
                      ifelse(grepl("2", path), "social relevance", ""))) %>%
    arrange(path) %>%
    select(variable, path, `Mdn [95% CI]`) %>%
    kable() %>%
    kableExtra::kable_styling()
}

get_paths_words = function(model, x_var, y_var) {
  create_paths_words(model, x_var, y_var) %>% 
    select(a1:a1b1_cov_a1b1, -contains("sd"), -contains("cor"), -starts_with("cov")) %>% 
    gather(path, value) %>% 
    article_cond_by(path) %>% 
    summarize(median = median(value),
              `Mdn [95% CI]` = sprintf("%.2f [%.2f, %.2f]", median(value), quantile(value, probs = .025), quantile(value, probs = .975))) %>%
    mutate(path = factor(path, levels = c("a1", "b1", "a1b1", "a1b1_cov_a1b1", "c", "c_prime")),
           variable = ifelse(grepl("1", path), "self-relevance",
                      ifelse(grepl("2", path), "social relevance", ""))) %>%
    arrange(path) %>%
    select(variable, path, `Mdn [95% CI]`) %>%
    kable() %>%
    kableExtra::kable_styling()
}

percent_mediated = function(model, x_var, y_var) {
  create_paths(model, x_var, y_var) %>% 
    select(a1b1_cov_a1b1, a2b2_cov_a2b2, c) %>% 
    gather(path, value) %>% 
    article_cond_by(path) %>% 
    summarize(median = median(value)) %>%
    select(path, median) %>%
    spread(path, median) %>%
    mutate(self = round((a1b1_cov_a1b1 / c) * 100, 0),
           social = round((a2b2_cov_a2b2 / c) * 100, 0),
           total = self + social) %>%
    select(self, social, total) %>%
    kable(caption = "percent mediated") %>%
    kableExtra::kable_styling()
}

percent_mediated_words = function(model, x_var, y_var) {
  create_paths_words(model, x_var, y_var) %>% 
    select(a1b1_cov_a1b1, c) %>% 
    gather(path, value) %>% 
    article_cond_by(path) %>% 
    summarize(median = median(value)) %>%
    select(path, median) %>%
    spread(path, median) %>%
    mutate(word_count = round((a1b1_cov_a1b1 / c) * 100, 0)) %>%
    select(word_count) %>%
    kable(caption = "percent mediated") %>%
    kableExtra::kable_styling()
}
```


## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#0a9396",
                      "other" = "#005f73")
palette_dv = c("self-relevance" = "#ee9b00",
               "social relevance" = "#005f73",
               "broadcast sharing" = "#5F0F40",
               "narrowcast sharing" = "#D295BF")
palette_sharing = c("broadcast sharing" = "#5F0F40",
               "narrowcast sharing" = "#D295BF")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
exploratory_dvs = read.csv("../data/study1_exploratory_dvs.csv", stringsAsFactors = FALSE)
```

# descriptives
## group ns
```{r}
exploratory_dvs %>%
  select(article_cond, SID) %>%
  unique() %>%
  group_by(article_cond) %>%
  summarize(n = n()) %>%
  spread(article_cond, n) %>%
  kable() %>%
  kable_styling()
```

# exploratory downstream effects {.tabset}
## petitions {.tabset}
> Do the interventions affect climate petition engagement?

```{r, fig.width=5, fig.height=4, results='asis'}
categories = unique(filter(exploratory_dvs, grepl("petition", scale_name))$scale_name)

for (category in categories){
  
  cat(paste0('\n\n### ', category, '{.tabset}\n\n'))  
  
  data_loop = exploratory_dvs %>%
    filter(scale_name == !!category) 
  
  if (category == "petition_link_clicks"){
    model = lm(value ~ article_cond, data = data_loop)
    
    print(table_model(model, lm = TRUE))
    
  } else {
    model = lmer(value ~ article_cond + (1 | SID) + (1 | item), data = data_loop)
    
    print(table_model(model))
  }
  
  predicted = ggeffects::ggpredict(model, terms = "article_cond") %>%
    data.frame()
  
  print(
    predicted %>%
      mutate(x = factor(x, levels = c("self", "control", "other"))) %>%
      ggplot(aes(x, predicted, color = x)) +
      geom_line(aes(group = 1), size = 1, color = "black") +
      geom_pointrange(aes(ymin = conf.low, ymax = conf.high), size = 1, linewidth = 1) +
      scale_color_manual(values = palette_condition) +
      labs(x = "", y = "predicted\n") +
      plot_aes +
      theme(legend.position = "none")
  )
}
```

## actions {.tabset}
> Do the interventions affect climate actions?

### across categories
```{r}
 model = lmer(value ~ article_cond + (1 | SID),
              data = filter(exploratory_dvs, grepl("action_env_impact", scale_name)))

table_model(model)
```

### by category 
```{r}
 model = lmer(value ~ article_cond * category + (1 | SID),
              data = filter(exploratory_dvs, grepl("action_env_impact", scale_name)))
cis = confint(emmeans::emmeans(model, specs = revpairwise ~ article_cond | category,
                        type = "response", adjust = "none", pbkrtest.limit = 19367))$contrasts %>%
  data.frame()

emmeans::emmeans(model, specs = revpairwise ~ article_cond | category,
                        type = "response", adjust = "none", pbkrtest.limit = 19367)$contrasts %>%
  data.frame() %>%
  left_join(., cis) %>%
  mutate(p = ifelse(p.value < .001, "< .001",
             ifelse(p.value == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p.value)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, lower.CL, upper.CL),
         df = round(df, 2),
         t.ratio = round(t.ratio, 2)) %>%
  rename("t" = t.ratio) %>%
  filter(!contrast == "self - other") %>%
  select(category, contrast, `b [95% CI]`, df, t, p) %>%
  kable() %>%
  kableExtra::kable_styling()
```

## person-level outcomes {.tabset}
> Do the interventions affect person-level outcomes?

```{r, fig.width=5, fig.height=4, results='asis'}
categories = unique(filter(exploratory_dvs, grepl("knowledge|self_efficacy", scale_name))$scale_name)

for (category in categories){
  
  cat(paste0('\n\n### ', category, '{.tabset}\n\n'))  
  
  data_loop = exploratory_dvs %>%
    filter(scale_name == !!category) 
  
  model = lm(value ~ article_cond, data = data_loop)
  
  print(table_model(model, lm = TRUE))
  
  predicted = ggeffects::ggpredict(model, terms = "article_cond") %>%
    data.frame()
  
  print(
    predicted %>%
      mutate(x = factor(x, levels = c("self", "control", "other"))) %>%
      ggplot(aes(x, predicted, color = x)) +
      geom_line(aes(group = 1), size = 1, color = "black") +
      geom_pointrange(aes(ymin = conf.low, ymax = conf.high), size = 1, linewidth = 1) +
      scale_color_manual(values = palette_condition) +
      labs(x = "", y = "predicted\n") +
      plot_aes +
      theme(legend.position = "none")
  )
}
```

# cite packages
```{r}
report::cite_packages()
```
