---
title: "Supplementary analyses: fMRI study 1"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, dpi = 300)

options(scipen=999)
```

In this report, we reproduce the analyses using data from fMRI study 1 reported in Supplementary Material.

# prep data {.tabset}
First, we load the relevant packages, define functions and plotting aesthetics, and load and tidy the data.


## load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, purrr, fs, knitr, lmerTest, ggeffects, kableExtra, boot, devtools, install = TRUE)
devtools::install_github("hadley/emo")
```

## define functions
```{r}
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

# MLM results table function
table_model = function(model_data) {
  model_data %>%
  broom.mixed::tidy(conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  select(-group, -effect) %>%
  mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
  mutate(term = gsub("cond", "", term),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("condother", "other", term),
         term = gsub("condself", "self", term),
         term = gsub("topichealth", "topic (health)", term),
         term = gsub("self_referential", "self-referential", term),
         term = gsub("self_relevance_z", "self-relevance", term),
         term = gsub("social_relevance_z", "social relevance", term),
         term = gsub(":", " x ", term),
         p = ifelse(p < .001, "< .001",
             ifelse(p > .999, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `b [95% CI]`, df, t, p)
}

simple_slopes = function(model, var, moderator, continuous = TRUE) {
  
  if (isTRUE(continuous)) {
    emmeans::emtrends(model, as.formula(paste("~", moderator)), var = var) %>%
      data.frame() %>%
      rename("trend" = 2) %>%
      mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", trend, asymp.LCL, asymp.UCL)) %>%
      select(!!moderator, `b [95% CI]`) %>%
      kable()  %>%
      kableExtra::kable_styling()
    
  } else {
    confint(emmeans::contrast(emmeans::emmeans(model, as.formula(paste("~", var, "|", moderator))), "revpairwise", by = moderator, adjust = "none")) %>%
      data.frame() %>%
      filter(grepl("control", contrast)) %>%
      mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, asymp.LCL, asymp.UCL)) %>%
      select(contrast, !!moderator, `b [95% CI]`) %>%
      arrange(contrast) %>%
      kable()  %>%
      kableExtra::kable_styling()
  }
}

```

## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#bb3e03",
                      "other" = "#005f73")

palette_sharing = c("#0a9396", "#ee9b00")
palette_roi = c("self-referential" = "#ee9b00",
               "mentalizing" = "#005f73")
palette_dv = c("self-relevance" = "#ee9b00",
               "social relevance" = "#005f73",
               "sharing" = "#56282D")
palette_topic = c("climate" = "#E6805E",
                 "health" = "#3A3357")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load and tidy data {.tabset}
```{r}
merged_all = read.csv("../data/study1_data.csv")

ratings_z = merged_all %>%
  select(pID, event, trial, self_relevance, social_relevance) %>%
  unique() %>%
  mutate(self_relevance_z = scale(self_relevance, center = TRUE, scale = TRUE),
         social_relevance_z = scale(social_relevance, center = TRUE, scale = TRUE))

merged = merged_all %>%
  filter(outlier == "no" | is.na(outlier)) %>%
  group_by(pID, atlas) %>%
  mutate(parameter_estimate_std = parameter_estimate / sd(parameter_estimate, na.rm = TRUE)) %>%
  left_join(., ratings_z)

merged_wide = merged %>%
  filter(atlas %in% c("self-referential", "mentalizing")) %>%
  select(site, pID, trial, topic, cond, value, self_relevance, self_relevance_z, social_relevance, social_relevance_z, atlas, parameter_estimate_std) %>%
  spread(atlas, parameter_estimate_std) %>%
  rename("self_referential" = `self-referential`)

merged_wide_alt = merged %>%
  filter(atlas %in% c("pnas_self", "pnas_mentalizing_nopc")) %>%
  select(site, pID, trial, topic, cond, value, self_relevance, self_relevance_z, social_relevance, social_relevance_z, atlas, parameter_estimate_std) %>%
  spread(atlas, parameter_estimate_std) %>%
  rename("self_referential" = pnas_self,
         "mentalizing" = pnas_mentalizing_nopc) 

```

<br><br>

# sensitivity analyses {.tabset}

Given the high correlation between the preregistered Neurosynth ROIs, we conducted sensitivity analyses using ROIs from [Scholz et al. (2017) A neural model of valuation and information virality](https://www.pnas.org/doi/10.1073/pnas.1615259114).

In order to maximize the differentiation between the self-referential and mentalizing ROIs, we removed the PCC/precuneus cluster from the mentalizing ROI as it overlapped with the self-referential ROI.


## ROI correlations
Compared to the preregistered Neurosynth ROIs (r = .94, 95% CI [.94, .94]), the correlation between the alternative ROIs are substantially reduced.

```{r}
merged_wide_alt %>%
  rmcorr::rmcorr(as.factor(pID), mentalizing, self_referential, data = .)
```

## H1 {.tabset}

> Is greater activity in the ROIs associated with higher self and social relevance ratings?


### self-referential ROI {.tabset}
`r emo::ji("check")`  H1a: Greater activity in the self-referential ROI will be associated with higher self-relevance ratings


```{r}
mod_h1a =  lmer(self_relevance ~ self_referential + (1 + self_referential | pID),
               data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h1a = table_model(mod_h1a)

table_h1a %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h1a)
```

### mentalizing ROI {.tabset}

`r emo::ji("check")` H1b: Greater activity in the mentalizing ROI will be associated with higher social relevance ratings


```{r}
mod_h1b = lmer(social_relevance ~ mentalizing + (1 + mentalizing | pID),
               data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h1b = table_model(mod_h1b)

table_h1b %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h1b)
```

### combined plot
```{r}
vals = seq(-4.5,4.5,.1)
predicted_h1 = ggeffects::ggpredict(mod_h1a, c("self_referential [vals]")) %>%
  data.frame() %>%
  mutate(roi = "self-referential",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1b, c("mentalizing [vals]")) %>%
              data.frame() %>%
              mutate(roi = "mentalizing",
                     variable = "social relevance"))

predicted_sub_h1 = ggeffects::ggpredict(mod_h1a, terms = c("self_referential [vals]", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "self-referential",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1b, c("mentalizing [vals]", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "mentalizing",
                     variable = "social relevance"))

predicted_h1 %>%
  ggplot(aes(x, predicted)) +
  stat_smooth(data = predicted_sub_h1, aes(group = group, color = roi), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = roi), alpha = .5, color = NA) +
  geom_line(aes(color = roi), size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_roi, guide = FALSE) +
  scale_fill_manual(name = "", values = palette_roi, guide = FALSE) +
  labs(x = "\nROI activity (SD)", y = "predicted rating\n") +
  plot_aes
```

## H4 {.tabset}

> Do the manipulations increase neural activity in brain regions associated with self-referential processing and mentalizing?


### self-referential ROI {.tabset}
`r emo::ji("check")` H4a: Self-focused intervention (compared to control) will increase brain activity in ROIs related to self-referential processes.

```{r}
mod_h4a = lmer(self_referential ~ cond + (1 + cond | pID),
              data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h4a = table_model(mod_h4a)

table_h4a %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h4a)
```

### mentalizing ROI {.tabset}

`r emo::ji("x")` H4b: Other-focused intervention (compared to control) will increase brain activity in ROIs related to mentalizing processes.


```{r}
mod_h4b = lmer(mentalizing ~ cond + (1 + cond | pID),
              data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h4b = table_model(mod_h4b)

table_h4b %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h4b)
```

### combined plot
```{r}
predicted_h4 = ggeffects::ggpredict(mod_h4a, c("cond")) %>%
  data.frame() %>%
  mutate(atlas = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("cond")) %>%
              data.frame() %>%
              mutate(atlas = "mentalizing")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         atlas = factor(atlas, levels = c("self-referential", "mentalizing")))

predicted_sub_h4 = ggeffects::ggpredict(mod_h4a, terms = c("cond", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(atlas = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("cond", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(atlas = "mentalizing")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         atlas = factor(atlas, levels = c("self-referential", "mentalizing")))

predicted_h4 %>%
  ggplot(aes(x = x, y = predicted)) +
  stat_summary(data = predicted_sub_h4, aes(group = group), fun = "mean", geom = "line",
               size = .1, color = "grey50") +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high), size = .75) +
  facet_grid(~atlas) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "ROI activity (SD)\n") +
  plot_aes
```

## H6 {.tabset}

> Is ROI activity positively related to sharing intentions?

### self-referential ROI {.tabset}

`r emo::ji("check")` Stronger activity in the self-referential ROI will be related to higher sharing intentions.

```{r}
mod_h6a = lmer(value ~ self_referential + (1 + self_referential | pID),
              data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h6a = table_model(mod_h6a)

table_h6a %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h6a)
```

### mentalizing ROI {.tabset}

`r emo::ji("check")` Stronger activation in the mentalizing ROI will be related to higher sharing intentions.

```{r}
mod_h6b = lmer(value ~ mentalizing + (1 + mentalizing | pID),
              data = merged_wide_alt,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h6b = table_model(mod_h6b)

table_h6b %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h6b)
```

### combined plot
```{r}
vals = seq(-4.5,4.5,.1)

predicted_h6 = ggeffects::ggpredict(mod_h6a, c("self_referential [vals]")) %>%
  data.frame() %>%
  mutate(roi = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h6b, c("mentalizing [vals]")) %>%
              data.frame() %>%
              mutate(roi = "mentalizing")) %>%
  mutate(roi = factor(roi, levels = c("self-referential", "mentalizing")))

predicted_sub_h6 = ggeffects::ggpredict(mod_h6a, terms = c("self_referential [vals]", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h6b, c("mentalizing [vals]", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "mentalizing")) %>%
  mutate(roi = factor(roi, levels = c("self-referential", "mentalizing")))

predicted_h6 %>%
  ggplot(aes(x = x, y = predicted, color = roi, fill = roi)) +
  stat_smooth(data = predicted_sub_h6, aes(group = group), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 2) +
  facet_grid(~roi) +
  scale_color_manual(name = "", values = palette_roi) +
  scale_fill_manual(name = "", values = palette_roi) +
  labs(y = "predicted sharing intention\n", x = "\nROI activity (SD)") +
  plot_aes +
  theme(legend.position = "none")
```

## H7 {.tabset}

> Is there an indirect effect of the condition on sharing intentions through activity in self-referential and mentalizing ROIs?

### prep data
```{r}
# source functions
source("indirectMLM.R")

# create self condition dataframe
data_med_self = merged_wide_alt %>%
  filter(!cond == "other") %>%
  mutate(cond = ifelse(cond == "self", 1, 0)) %>%
  select(pID, site, trial, cond, value, self_referential) %>%
  data.frame()

# create social condition dataframe
data_med_other = merged_wide_alt %>%
  filter(!cond == "self") %>%
  mutate(cond = ifelse(cond == "other", 1, 0)) %>%
  select(pID, site, trial, cond, value, mentalizing) %>%
  data.frame()

# define variables
y_var = "value"
```

### self condition {.tabset}

`r emo::ji("check")` H7a: The effect of self-focused intervention on sharing intention will be mediated by increased activity in the self-referential ROI.

```{r}
model_name = "mediation_self"
data = data_med_self

if (file.exists(sprintf("models/model_%s_alternative.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s_alternative.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "cond", mediator = "self_referential", group.id = "pID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s_alternative.RDS", model_name))
}

indirect.mlm.summary(get(model_name))
```

### other condition {.tabset}

`r emo::ji("x")` H7b: The effect of other-focused intervention on sharing intention will be mediated by increased activity in the mentalizing ROI.

```{r}
model_name = "mediation_other"
data = data_med_other

if (file.exists(sprintf("models/model_%s_alternative.RDS", model_name))) {
  assign(get("model_name"), readRDS(sprintf("models/model_%s_alternative.RDS", model_name)))
} else {
  assign(get("model_name"), boot(data = data, statistic = indirect.mlm, R = 500,
                                 y = y_var, x = "cond", mediator = "mentalizing", group.id = "pID",
                                 between.m = F, uncentered.x = F))
  saveRDS(eval(parse(text = model_name)), sprintf("models/model_%s_alternative.RDS", model_name))
}

indirect.mlm.summary(get(model_name))
```

<br><br>

## combined table
```{r}
table_h1a %>% mutate(DV = "H1a: Self-relevance") %>%
  bind_rows(table_h1b %>% mutate(DV = "H1b: Social relevance")) %>%
  bind_rows(table_h4a %>% mutate(DV = "H4a: Self-referential ROI")) %>%
  bind_rows(table_h4b %>% mutate(DV = "H4b: Mentalizing ROI")) %>%
  bind_rows(table_h6a %>% mutate(DV = "H6a: Sharing intention")) %>%
  bind_rows(table_h6b %>% mutate(DV = "H6b: Sharing intention")) %>%
  select(DV, everything()) %>%
  kable() %>%
  kable_styling()
```

# moderation by article topic {.tabset}

These analyses explore whether the analyses reported in study 1 of the main manuscript are moderated by article topic (health or climate).

## H1 {.tabset}

> Are the relationships between ROI activity and self and social relevance ratings moderated by article topic?


### self-referential ROI {.tabset}
There is a main effect of topic, such that health articles elicited greater activity in the self-referential ROI compared to climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h1am =  lmer(self_relevance ~ self_referential * topic + (1 + topic | pID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h1am = table_model(mod_h1am)

table_h1am %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h1am)
```

### mentalizing ROI {.tabset}

There is a main effect of topic, such that health articles elicited greater activity in the mentalizing ROI compared to climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h1bm = lmer(social_relevance ~ mentalizing * topic + (1 + mentalizing | pID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h1bm = table_model(mod_h1bm)

table_h1bm %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h1bm)
```

### combined plot
```{r}
vals = seq(-4.5,4.5,.1)

predicted_h1m = ggeffects::ggpredict(mod_h1am, c("self_referential [vals]", "topic")) %>%
  data.frame() %>%
  mutate(roi = "self-referential",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1bm, c("mentalizing [vals]", "topic")) %>%
              data.frame() %>%
              mutate(roi = "mentalizing",
                     variable = "social relevance"))


predicted_sub_h1m = ggeffects::ggpredict(mod_h1am, terms = c("self_referential [vals]", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "self-referential",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1bm, c("mentalizing [vals]", "topic", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "mentalizing",
                     variable = "social relevance")) 

predicted_h1m %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  stat_smooth(data = predicted_sub_h1m, aes(group = interaction(group, facet)),
              geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .3, color = NA) +
  geom_line(size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_topic) +
  scale_fill_manual(name = "", values = palette_topic) +
  labs(x = "\nROI activity (SD)", y = "predicted rating\n") +
  plot_aes +
  theme(legend.key.width=unit(2,"cm"))
```

## H2 {.tabset}
> Are the effects of the experimental manipulations on relevance moderated by article topic?

### self-relevance {.tabset}
There is a main effect of topic such that health articles are rated as more self-relevant than climate articles.

The was also an interaction such that the effect of the self-focused condition on self-relevance was weaker for health articles.

```{r}
mod_h2am = lmer(self_relevance ~ cond * topic + (1 + topic | pID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2am = table_model(mod_h2am)

table_h2am %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h2am)
```

### social relevance {.tabset}

There is a main effect of topic such that health articles are rated as more socially relevant than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h2bm = lmer(social_relevance ~ cond * topic + (1 + topic | pID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2bm = table_model(mod_h2bm)

table_h2bm %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h2bm)
```

### combined plot
```{r}
predicted_h2m = ggeffects::ggpredict(mod_h2am, c("cond", "topic")) %>%
  data.frame() %>%
  mutate(model = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h2bm, c("cond", "topic")) %>%
              data.frame() %>%
              mutate(model = "social relevance")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

predicted_sub_h2m = ggeffects::ggpredict(mod_h2am, terms = c("cond", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(model = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h2bm, c("cond", "topic", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(model = "social relevance")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other"))) 
  
predicted_h2m %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(data = predicted_sub_h2m, aes(group = interaction(group, facet)), fun = "mean", geom = "line", size = .1, alpha = .5) +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, group = group),
                  size = .75) +
  facet_grid(~model) +
  scale_color_manual(name = "", values = palette_topic) +
  labs(x = "", y = "predicted rating\n") +
  plot_aes +
  theme(legend.position = c(.85, .15))
```

## H3 {.tabset}

> Are the relationships between self and social relevance and sharing intentions moderated by article topic?

The relationship between self-relevance and sharing intentions was not moderated by topic.

However, the relationship between social relevance and sharing intentions was slightly stronger for health articles compared to climate articles.

```{r}
mod_h3m = lmer(value ~ self_relevance_z * topic + social_relevance_z * topic + (1 + self_relevance_z + social_relevance_z | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted_h3m = ggeffects::ggpredict(mod_h3m, c("self_relevance_z", "topic")) %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h3m, c("social_relevance_z", "topic")) %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

predicted_sub_h3m = ggeffects::ggpredict(mod_h3m, terms = c("self_relevance_z", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h3m, c("social_relevance_z", "topic", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

predicted_h3m %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  stat_smooth(data = predicted_sub_h3m, aes(group = interaction(group, facet)),
              geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .3, color = NA) +
  geom_line(size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_topic) +
  scale_fill_manual(name = "", values = palette_topic) +
  labs(x = "\nrating (SD)", y = "predicted sharing intention\n") +
  plot_aes +
  theme(legend.key.width=unit(2,"cm"))
```

### model table
```{r}
table_h3m = table_model(mod_h3m)

table_h3m %>%
    kable()  %>%
    kableExtra::kable_styling()
```

### summary
```{r}
summary(mod_h3m)
```

## H4 {.tabset}

> Are the effects of the experimental manipulations on ROI activity moderated by article topic?


### self-referential ROI {.tabset}
There is a main effect of topic, such that health articles elicited greater activity in the self-referential ROI compared to climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h4am = lmer(self_referential ~ cond * topic + (1 + cond + topic | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h4am = table_model(mod_h4am)

table_h4am %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h4am)
```

### mentalizing ROI {.tabset}

There is a main effect of topic, such that health articles elicited greater activity in the mentalizing ROI compared to climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h4bm = lmer(mentalizing ~ cond * topic + (1 + cond + topic | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h4bm = table_model(mod_h4bm)

table_h4bm %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h4bm)
```

### combined plot
```{r}
predicted_h4m = ggeffects::ggpredict(mod_h4am, c("cond", "topic")) %>%
  data.frame() %>%
  mutate(atlas = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h4bm, c("cond", "topic")) %>%
              data.frame() %>%
              mutate(atlas = "mentalizing")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         atlas = factor(atlas, levels = c("self-referential", "mentalizing")))

predicted_sub_h4m = ggeffects::ggpredict(mod_h4am, terms = c("cond", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(atlas = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h4bm, c("cond", "topic", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(atlas = "mentalizing")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         atlas = factor(atlas, levels = c("self-referential", "mentalizing")))

predicted_h4m %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(data = predicted_sub_h4m, aes(group = interaction(group, facet)), fun = "mean", geom = "line", size = .1) +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1, position = position_dodge(.1)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, group = group),
                  size = .75, position = position_dodge(.1)) +
  facet_grid(~atlas) +
  scale_color_manual(name = "", values = palette_topic) +
  labs(x = "", y = "ROI activity (SD)\n") +
  plot_aes +
  theme(legend.position = c(.18, .95))
```

## H5 {.tabset}
> Are the effect of the experimental manipulations on sharing intentions moderated by article topic?

There is a main effect of topic, such that health articles have higher sharing intentions than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h5m = lmer(value ~ cond * topic + (1 + cond + topic | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted_h5m = ggeffects::ggpredict(mod_h5m, c("cond", "topic")) %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

predicted_sub_h5m = ggeffects::ggpredict(mod_h5m, terms = c("cond", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))
  
predicted_h5m %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(data = predicted_sub_h5m, aes(group = interaction(group, facet)), fun = "mean", geom = "line", size = .1) +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, group = group),
                  size = .75) +
  scale_color_manual(name = "", values = palette_topic) +
  labs(x = "", y = "predicted sharing intention\n") +
  plot_aes +
  theme(legend.position = c(.85, .15))
 
```

### model table
```{r}
table_h5m = table_model(mod_h5m)

table_h5m %>%
    kable()  %>%
    kableExtra::kable_styling()
```

### summary
```{r}
summary(mod_h5m)
```

## H6 {.tabset}

> Are the relationships between ROI activity positively and sharing intentions moderated by article topic?

### self-referential ROI {.tabset}

There is a main effect of topic, such that health articles have higher sharing intentions than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h6am = lmer(value ~ self_referential * topic + (1 + self_referential + topic | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h6am = table_model(mod_h6am)

table_h6am %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h6am)
```

### mentalizing ROI {.tabset}

There is a main effect of topic, such that health articles have higher sharing intentions than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h6bm = lmer(value ~ mentalizing * topic + (1 + topic | pID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h6bm = table_model(mod_h6bm)

table_h6bm %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h6bm)
```

### combined plot
```{r}
vals = seq(-4.5,4.5,.1)

predicted_h6m = ggeffects::ggpredict(mod_h6am, c("self_referential [vals]", "topic")) %>%
  data.frame() %>%
  mutate(atlas = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h6bm, c("mentalizing [vals]", "topic")) %>%
              data.frame() %>%
              mutate(atlas = "mentalizing")) %>%
  mutate(atlas = factor(atlas, levels = c("self-referential", "mentalizing")))

predicted_sub_h6m = ggeffects::ggpredict(mod_h6am, terms = c("self_referential [vals]", "topic", "pID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "self-referential") %>%
  bind_rows(ggeffects::ggpredict(mod_h6bm, c("mentalizing [vals]", "topic", "pID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "mentalizing")) %>%
  mutate(roi = factor(roi, levels = c("self-referential", "mentalizing")))

predicted_h6m %>%
  ggplot(aes(x = x, y = predicted, color = group, fill = group)) +
  stat_smooth(data = predicted_sub_h6m, aes(group = interaction(group, facet)),
              geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .3, color = NA) +
  geom_line(size = 2) +
  facet_grid(~atlas) +
  scale_color_manual(name = "", values = palette_topic) +
  scale_fill_manual(name = "", values = palette_topic) +
  labs(y = "predicted sharing intention\n", x = "\nROI activity (SD)") +
  plot_aes +
  theme(legend.key.width=unit(2,"cm"))
```

## combined table
```{r}
table_h1am %>% mutate(DV = "H1a: Self-relevance") %>%
  bind_rows(table_h1bm %>% mutate(DV = "H1b: Social relevance")) %>%
  bind_rows(table_h2am %>% mutate(DV = "H2a: Self-relevance")) %>%
  bind_rows(table_h2bm %>% mutate(DV = "H2b: Social relevance")) %>%
  bind_rows(table_h3m %>% mutate(DV = "H3a-b: Sharing intention")) %>%
  bind_rows(table_h4am %>% mutate(DV = "H4a: Self-referential ROI")) %>%
  bind_rows(table_h4bm %>% mutate(DV = "H4b: Mentalizing ROI")) %>%
  bind_rows(table_h5m %>% mutate(DV = "H5: Sharing intention")) %>%
  bind_rows(table_h6am %>% mutate(DV = "H6a: Sharing intention")) %>%
  bind_rows(table_h6bm %>% mutate(DV = "H6b: Sharing intention")) %>%
  select(DV, everything()) %>%
  kable() %>%
  kable_styling()
```

# cite packages
```{r}
report::cite_packages()
```
