---
title: "Study 3 sensitivity analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, cache = FALSE, dpi = 300)

options(scipen=999)
```

In this report, we reproduce the sensitivity analyses testing H4-6 in Study 3 in control and value ROIs.

# prep data {.tabset}
First, we load the relevant packages, define functions and plotting aesthetics, and load and tidy the data.

## load packages
```{r}
library(pacman)
pacman::p_load(tidyverse, purrr, fs, knitr, lmerTest, ggeffects, kableExtra, boot, devtools, brms, tidybayes, install = TRUE)
```

## define functions
```{r}
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

# MLM results table function
table_model = function(model_data, print = TRUE) {
  table = model_data %>%
    broom.mixed::tidy(conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
    mutate(term = gsub("article_cond", "", term),
           term = gsub("\\(Intercept\\)", "intercept", term),
           term = gsub("other$", "other - control", term),
           term = gsub("self$", "self - control", term),
           term = gsub("siteUSA", "sample (USA)", term),
           term = gsub("value", "value", term),
           term = gsub("value", "value", term),
           term = gsub("msg_rel_self_z", "self-relevance", term),
           term = gsub("msg_rel_social_z", "social relevance", term),
           term = gsub("topichealth", "topic (health)", term),
           term = gsub(":", " x ", term),
           term = gsub("sample \\(USA\\) x social relevance", "social relevance x sample (USA)", term),
           p = ifelse(p < .001, "< .001",
               ifelse(p > .999, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
    select(term, `b [95% CI]`, df, t, p) %>%
    arrange(term)
  
  if (isTRUE(print)) {
    table  %>%
      kable() %>%
      kableExtra::kable_styling()
  } else {
    table
  }
}

simple_slopes = function(model, var, moderator, continuous = TRUE) {
  
  if (isTRUE(continuous)) {
    emmeans::emtrends(model, as.formula(paste("~", moderator)), var = var) %>%
      data.frame() %>%
      rename("trend" = 2) %>%
      mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", trend, asymp.LCL, asymp.UCL)) %>%
      select(!!moderator, `b [95% CI]`) %>%
      kable()  %>%
      kableExtra::kable_styling()
    
  } else {
    confint(emmeans::contrast(emmeans::emmeans(model, as.formula(paste("~", var, "|", moderator))), "revpairwise", by = moderator, adjust = "none")) %>%
      data.frame() %>%
      filter(grepl("control", contrast)) %>%
      mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, asymp.LCL, asymp.UCL)) %>%
      select(contrast, !!moderator, `b [95% CI]`) %>%
      arrange(contrast) %>%
      kable()  %>%
      kableExtra::kable_styling()
  }
}
```

## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#0a9396",
                      "other" = "#005f73")

palette_roi = c("value" = "#0a9396",
               "auditory" = "grey50")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```


## load and tidy data {.tabset}
```{r}
merged_all = read.csv("../data/study3_data_sensitivity.csv")

ratings_z = merged_all %>%
  select(SID, trial, article_number, article_cond, msg_rel_self, msg_rel_social, msg_share) %>%
  unique() %>%
  mutate(msg_share_z = scale(msg_share, scale = TRUE, center = TRUE),
         msg_rel_self_z = scale(msg_rel_self, center = TRUE, scale = TRUE),
         msg_rel_social_z = scale(msg_rel_social, center = TRUE, scale = TRUE))

merged = merged_all %>%
  filter(outlier == "no" | is.na(outlier)) %>%
  group_by(SID, atlas) %>%
  mutate(parameter_estimate_std = parameter_estimate / sd(parameter_estimate, na.rm = TRUE)) %>%
  left_join(., ratings_z)

merged_wide = merged %>%
  select(SID, site, trial, article_number, topic, article_cond, msg_share, msg_share_z,
         msg_rel_self, msg_rel_self_z, msg_rel_social, msg_rel_social_z, atlas, parameter_estimate_std) %>%
  spread(atlas, parameter_estimate_std)
```

# value ROI
## H4: relevance ~ ROI activity {.tabset}
### self-relevance {.tabset}

```{r}
mod_h4a =  lmer(msg_rel_self_z ~ value + (1 + value | SID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h4a)
```

#### summary
```{r}
summary(mod_h4a)
```

### social {.tabset}

```{r}
mod_h4b = lmer(msg_rel_social_z ~ value + (1 + value | SID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h4b)
```

#### summary
```{r}
summary(mod_h4b)
```

### plot
```{r}
predicted_h4_value = ggeffects::ggpredict(mod_h4a, c("value [-4.5:5]")) %>%
  data.frame() %>%
  mutate(roi = "value",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("value [-4.5:5]")) %>%
              data.frame() %>%
              mutate(roi = "value",
                     variable = "social relevance"))

predicted_sub_h4_value = ggeffects::ggpredict(mod_h4a, terms = c("value [-4.5:5]", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "value",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("value [-4.5:5]", "SID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "value",
                     variable = "social relevance"))

predicted_h4_value %>%
  ggplot(aes(x, predicted)) +
  stat_smooth(data = predicted_sub_h4_value, aes(group = group, color = roi), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = roi), alpha = .5, color = NA) +
  geom_line(aes(color = roi), size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_roi, guide = FALSE) +
  scale_fill_manual(name = "", values = palette_roi, guide = FALSE) +
  labs(x = "\nROI activity (SD)", y = "predicted rating (SD)\n") +
  plot_aes
```

## H5: sharing ~ ROI activity {.tabset}
### value ROI {.tabset}

```{r}
mod_h5a = lmer(msg_share_z ~ value + (1 + value | SID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h5a)
```

#### summary
```{r}
summary(mod_h5a)
```

### plot
```{r, fig.width = 5, fig.height = 4}
vals = seq(-4.5, 4.5, .1)

predicted_h5_value = ggeffects::ggpredict(mod_h5a, c("value [vals]")) %>%
  data.frame() %>%
  mutate(roi = "value",
         variable = "narrowcast sharing")

predicted_sub_h5_value = ggeffects::ggpredict(mod_h5a, terms = c("value [vals]", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "value",
         variable = "narrowcast sharing")

predicted_h5_value %>%
  ggplot(aes(x = x, y = predicted, color = roi, fill = roi)) +
  stat_smooth(data = predicted_sub_h5_value, aes(group = group), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 2) +
  scale_color_manual(name = "", values = palette_roi) +
  scale_fill_manual(name = "", values = palette_roi) +
  labs(y = "predicted sharing intention (SD)\n", x = "\nROI activity (SD)") +
  plot_aes +
  theme(legend.position = "none")
```


## H6 ROI activity ~ intervention condition {.tabset}
### value ROI {.tabset}

```{r}
mod_h6a = lmer(value ~ article_cond + (1 + article_cond | SID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h6a)
```

#### summary
```{r}
summary(mod_h6a)
```

### plot
```{r}
predicted_h6_value = ggeffects::ggpredict(mod_h6a, c("article_cond")) %>%
  data.frame() %>%
  mutate(atlas = "value")

predicted_sub_h6_value = ggeffects::ggpredict(mod_h6a, terms = c("article_cond", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(atlas = "value") 

predicted_h6_value %>%
  ggplot(aes(x = x, y = predicted)) +
  stat_summary(data = predicted_sub_h6_value, aes(group = group), fun = "mean", geom = "line",
               size = .1, color = "grey50") +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high), size = .75) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "predicted ROI activity (SD)\n") +
  plot_aes
```

# auditory ROI
## H4: relevance ~ ROI activity {.tabset}
### self-relevance {.tabset}
```{r}
mod_h4a =  lmer(msg_rel_self_z ~ auditory + (1 + auditory | SID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h4a)
```

#### summary
```{r}
summary(mod_h4a)
```

### social {.tabset}

```{r}
mod_h4b = lmer(msg_rel_social_z ~ auditory + (1 + auditory | SID),
               data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h4b)
```

#### summary
```{r}
summary(mod_h4b)
```

### plot
```{r}
predicted_h4_auditory = ggeffects::ggpredict(mod_h4a, c("auditory [-4.5:5]")) %>%
  data.frame() %>%
  mutate(roi = "auditory",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("auditory [-4.5:5]")) %>%
              data.frame() %>%
              mutate(roi = "auditory",
                     variable = "social relevance"))

predicted_sub_h4_auditory = ggeffects::ggpredict(mod_h4a, terms = c("auditory [-4.5:5]", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "auditory",
         variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h4b, c("auditory [-4.5:5]", "SID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "auditory",
                     variable = "social relevance"))

predicted_h4_auditory %>%
  ggplot(aes(x, predicted)) +
  stat_smooth(data = predicted_sub_h4_auditory, aes(group = group, color = roi), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = roi), alpha = .5, color = NA) +
  geom_line(aes(color = roi), size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_roi, guide = FALSE) +
  scale_fill_manual(name = "", values = palette_roi, guide = FALSE) +
  labs(x = "\nROI activity (SD)", y = "predicted rating (SD)\n") +
  plot_aes
```

## H5: sharing ~ ROI activity {.tabset}
### value ROI {.tabset}

```{r}
mod_h5a = lmer(msg_share_z ~ auditory + (1 + auditory | SID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h5a)
```

#### summary
```{r}
summary(mod_h5a)
```

### plot
```{r, fig.width = 5, fig.height = 4}
vals = seq(-4.5, 4.5, .1)

predicted_h5_auditory = ggeffects::ggpredict(mod_h5a, c("auditory [vals]")) %>%
  data.frame() %>%
  mutate(roi = "auditory",
         variable = "narrowcast sharing")

predicted_sub_h5_auditory = ggeffects::ggpredict(mod_h5a, terms = c("auditory [vals]", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "auditory",
         variable = "narrowcast sharing")

predicted_h5_auditory %>%
  ggplot(aes(x = x, y = predicted, color = roi, fill = roi)) +
  stat_smooth(data = predicted_sub_h5_auditory, aes(group = group), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 2) +
  scale_color_manual(name = "", values = palette_roi) +
  scale_fill_manual(name = "", values = palette_roi) +
  labs(y = "predicted sharing intention (SD)\n", x = "\nROI activity (SD)") +
  plot_aes +
  theme(legend.position = "none")
```


## H6 ROI activity ~ intervention condition {.tabset}
### auditory ROI {.tabset}

```{r}
mod_h6a = lmer(auditory ~ article_cond + (1 + article_cond | SID),
              data = merged_wide,
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_model(mod_h6a)
```

#### summary
```{r}
summary(mod_h6a)
```

### plot
```{r}
predicted_h6_auditory = ggeffects::ggpredict(mod_h6a, c("article_cond")) %>%
  data.frame() %>%
  mutate(atlas = "auditory")

predicted_sub_h6_auditory = ggeffects::ggpredict(mod_h6a, terms = c("article_cond", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(atlas = "auditory") 

predicted_h6_auditory %>%
  ggplot(aes(x = x, y = predicted)) +
  stat_summary(data = predicted_sub_h6_auditory, aes(group = group), fun = "mean", geom = "line",
               size = .1, color = "grey50") +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high), size = .75) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "predicted ROI activity (SD)\n") +
  plot_aes
```


# combined figure
```{r}
predicted = predicted_h4_value %>%
  bind_rows(predicted_h5_value) %>%
  bind_rows(predicted_h4_auditory) %>%
  bind_rows(predicted_h5_auditory)

predicted_sub = predicted_sub_h4_value %>%
  bind_rows(predicted_sub_h5_value) %>%
  bind_rows(predicted_sub_h4_auditory) %>%
  bind_rows(predicted_sub_h5_auditory)

predicted %>%
  ggplot(aes(x, predicted, color = roi)) +
  stat_smooth(data = predicted_sub, aes(group = interaction(group, roi)), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = roi), alpha = .5, color = NA) +
  geom_line(aes(color = roi), size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_roi) +
  scale_fill_manual(name = "", values = palette_roi) +
  labs(x = "\nROI activity (SD)", y = "predicted rating (SD)\n") +
  plot_aes
```

# cite packages
```{r}
report::cite_packages()
```

