---
title: "Supplementary analyses: follow-up behavioral study 2"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 300)
options(scipen = 999)
set.seed(65)
```

In this report, we reproduce the analyses using data from follow-up behavioral study 2 reported in Supplementary Material.

# prep data {.tabset}
First, we load the relevant packages, define functions and plotting aesthetics, and load and tidy the data.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, purrr, fs, knitr, lmerTest, ggeffects, kableExtra, boot, devtools, EMAtools, install = TRUE)
devtools::install_github("hadley/emo")
```

## define functions
```{r}
# MLM results table function
table_model = function(model_data) {
  model_data %>%
  broom.mixed::tidy(conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "t" = statistic,
         "p" = p.value) %>%
  select(-group, -effect) %>%
  mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
  mutate(term = gsub("cond", "", term),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("article_other", "other", term),
         term = gsub("article_self", "self", term),
         term = gsub("topichealth", "topic (health)", term),
         term = gsub("msg_rel_self", "self-relevance", term),
         term = gsub("msg_rel_social", "social relevance", term),
         term = gsub(":", " x ", term),
         p = ifelse(p < .001, "< .001",
             ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  select(term, `b [95% CI]`, df, t, p)
}

# simple effects function
simple_effects = function(model, sharing = FALSE) {
  if(sharing == FALSE) {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("control", contrast)) %>%
      select(contrast, group, estimate, p.value)
  } else {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group + sharing_type),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("- control", contrast)) %>%
      filter(!grepl("^control", contrast)) %>%
      extract(contrast, c("exp_sharing", "control_sharing"), ".* (0|1) - control (0|1)", remove = FALSE) %>%
      filter(exp_sharing == control_sharing) %>%
      mutate(sharing_type = ifelse(exp_sharing == 0, "broadcast", "narrowcast"),
             contrast = gsub("0|1", "", contrast)) %>%
      select(contrast, sharing_type, group, estimate, p.value)
  }
  
  results %>%
    mutate(p.value = ifelse(p.value < .001, "< .001",
                      ifelse(p.value == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p.value))))) %>%
    kable(digits = 2) %>%
    kableExtra::kable_styling()
}
```


## define aesthetics
```{r}
palette_condition = c("#ee9b00", "#bb3e03", "#005f73")
palette_topic = c("climate" = "#E6805E",
                 "health" = "#3A3357")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
data = read.csv("../data/study2_data.csv", stringsAsFactors = FALSE) %>%
  mutate(article_cond = ifelse(article_cond == "social", "other", article_cond))

n_words = read.csv("../data/study2_n_words.csv", stringsAsFactors = FALSE) %>%
  mutate(article_cond = ifelse(article_cond == "social", "other", article_cond))
```

# moderation by article topic, comment group only {.tabset}

These analyses explore whether the analyses reported in follow-up behavioral study 2 of the main manuscript are moderated by article topic (health or climate). We focus on the comment group only because this is the only group for which the intervention was effective.

```{r}
data_comment = data %>%
  filter(group == "comment") %>%
  select(-group)
```


## H2 {.tabset}
> Are the effects of the experimental manipulations on relevance moderated by article topic?

### self-relevance {.tabset}
There is a main effect of topic such that health articles are rated as more self-relevant than climate articles.

The was also an interaction such that the effect of the self-focused condition on self-relevance was weaker for health articles.

```{r}
mod_h2a = lmer(msg_rel_self ~ article_cond * topic + (1 | SID),
               data = filter(data_comment, sharing_type == 0), 
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2a = table_model(mod_h2a)

table_h2a %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h2a)
```

### social relevance {.tabset}

There is a main effect of topic such that health articles are rated as more socially relevant than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h2b = lmer(msg_rel_social ~ article_cond * topic + (1 | SID),
               data = filter(data_comment, sharing_type == 0), 
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2b = table_model(mod_h2b)

table_h2b %>%
    kable()  %>%
    kableExtra::kable_styling()
```

#### summary
```{r}
summary(mod_h2b)
```

### combined plot
```{r}
predicted_h2 = ggeffects::ggpredict(mod_h2a, c("article_cond", "topic")) %>%
  data.frame() %>%
  mutate(model = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h2b, c("article_cond", "topic")) %>%
              data.frame() %>%
              mutate(model = "social relevance")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

ind_data_h2 = data_comment %>%
  rename("x" = article_cond,
         "group" = topic) %>%
  gather(model, predicted, msg_rel_self, msg_rel_social) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         model = gsub("msg_rel_self", "self-relevance", model),
         model = gsub("msg_rel_social", "social relevance", model))
  
(plot_h2 = predicted_h2 %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(data = ind_data_h2, aes(group = interaction(SID, group)), fun = "mean", geom = "line", size = .1, alpha = .75) +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1, position = position_dodge(.1)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, group = group),
                  size = .75, position = position_dodge(.1)) +
  facet_grid(~model) +
  scale_color_manual(name = "", values = palette_topic) +
  labs(x = "", y = "predicted rating\n") +
  plot_aes +
  theme(legend.position = c(.9, .2)))
```

## H3 {.tabset}

> Are the relationships between self and social relevance and sharing intentions moderated by article topic?

The relationship between self-relevance and sharing intentions was not moderated by topic.

However, the relationship between social relevance and sharing intentions was slightly stronger for health articles compared to climate articles.

```{r}
mod_h3 = lmer(msg_share ~ msg_rel_self * topic + msg_rel_social * topic + (1 + msg_rel_self | SID),
              data = data_comment,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted = ggeffects::ggpredict(mod_h3, c("msg_rel_self", "topic")) %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h3, c("msg_rel_social", "topic")) %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

points = data_comment %>%
  rename("predicted" = msg_share,
         "group" = topic) %>%
  gather(variable, x, msg_rel_self, msg_rel_social) %>%
  mutate(variable = gsub("msg_rel_self", "self-relevance", variable),
         variable = gsub("msg_rel_social", "social relevance", variable))

(plot_rel_sharing = predicted %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  stat_smooth(data = points, aes(group = interaction(SID, group)), geom ='line', method = "lm", alpha = .1, size = 1, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2, color = NA) +
  geom_line(size = 2) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_topic) +
  scale_fill_manual(name = "", values = palette_topic) +
  labs(x = "\nrating", y = "predicted sharing intention\n") +
  plot_aes)
```

### model table
```{r}
table_h3 = table_model(mod_h3)

table_h3 %>%
    kable()  %>%
    kableExtra::kable_styling()
```

### summary
```{r}
summary(mod_h3)
```

## H5 {.tabset}
> Are the effect of the experimental manipulations on sharing intentions moderated by article topic?

There is a main effect of topic, such that health articles have higher sharing intentions than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h5 = lmer(msg_share ~ article_cond * topic + (1 | SID),
              data = data_comment,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted_h5 = ggeffects::ggpredict(mod_h5, c("article_cond", "topic")) %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

ind_data_h5 = data_comment %>%
  rename("x" = article_cond,
         "predicted" = msg_share,
         "group" = topic) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

predicted_h5 %>%
  ggplot(aes(x = x, y = predicted, color = group)) +
  stat_summary(data = ind_data_h5, aes(group = interaction(SID, group)), fun = "mean", geom = "line", size = .1, alpha = .75) +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1, position = position_dodge(.1)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, group = group),
                  size = .75, position = position_dodge(.1)) +
  scale_color_manual(name = "", values = palette_topic) +
  labs(x = "", y = "predicted sharing intention\n") +
  plot_aes +
  theme(legend.position = c(.9, .2))
 
```

### model table
```{r}
table_h5 = table_model(mod_h5)

table_h5 %>%
    kable()  %>%
    kableExtra::kable_styling()
```

### summary
```{r}
summary(mod_h5)
```

## combined table
```{r}
table_h2a %>% mutate(DV = "H2a: Self-relevance") %>%
  bind_rows(table_h2b %>% mutate(DV = "H2b: Social relevance")) %>%
  bind_rows(table_h3 %>% mutate(DV = "H3a-b: Sharing intention")) %>%
  bind_rows(table_h5 %>% mutate(DV = "H5: Sharing intention")) %>%
  select(DV, everything()) %>%
  kable() %>%
  kable_styling()
```

# cite packages
```{r}
report::cite_packages()
```
