---
title: "Study 2 analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = TRUE, cache = FALSE, dpi = 300)

options(scipen=999)
```

In this report, we reproduce the Study 2 analyses testing H1 and H3 with sharing behavior.

# prep data {.tabset}
First, we load the relevant packages, define functions and plotting aesthetics, and load and tidy the data.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, kableExtra, lmerTest, report, EMAtools, install = TRUE)
```

## define functions
```{r}
# MLM results table function
table_model = function(model_data, eff_size = FALSE, word_count = TRUE, reversed = FALSE, logistic = FALSE) {

  results = model_data %>%
    broom.mixed::tidy(conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
    mutate(term = gsub("article_cond", "", term),
           term = gsub("\\(Intercept\\)", "control", term),
           term = gsub("sharing_type", "sharing type (broadcast)", term),
           term = gsub("msg_rel_self_z", "self-relevance", term),
           term = gsub("msg_rel_social_z", "social relevance", term),
           term = gsub("topichealth", "topic (health)", term),
           term = gsub("n_c", "word count", term),
           term = gsub(":", " x ", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) 
  
  if (word_count == TRUE) {
    results = results %>%
      mutate(term = gsub("control", "intercept", term))
  }

  if (reversed == TRUE) {
    results = results %>%
      mutate(term = gsub("broadcast", "narrowcast", term))
  }
  
  if (eff_size == TRUE) {
    eff_size = lme.dscore(model_data, data = data, type = "lme4") %>%
      rownames_to_column(var = "term") %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type (broadcast)", term),
             term = gsub("msg_rel_self", "self-relevance", term),
             term = gsub("msg_rel_social", "social relevance", term),
             term = gsub("topichealth", "topic (health)", term),
             term = gsub(":", " x ", term),
             d = sprintf("%.2f", d)) %>%
      select(term, d)
    
    results %>%
      left_join(., eff_size) %>%
      mutate(d = ifelse(is.na(d), "--", d)) %>%
      select(term, `b [95% CI]`, d, df, t, p)
    
  } else if (logistic == TRUE) {
    results %>%
      rename("z" = t) %>%
      select(term, `b [95% CI]`, z, p)
    
  } else {
    results %>%
      select(term, `b [95% CI]`, df, t, p)
  }
}

# simple effects function
simple_effects = function(model, sharing = FALSE) {
  if(sharing == FALSE) {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("control", contrast)) %>%
      select(contrast, group, estimate, p.value)
  } else {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group + sharing_type),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("- control", contrast)) %>%
      filter(!grepl("^control", contrast)) %>%
      extract(contrast, c("exp_sharing", "control_sharing"), ".* (0|1) - control (0|1)", remove = FALSE) %>%
      filter(exp_sharing == control_sharing) %>%
      mutate(sharing_type = ifelse(exp_sharing == 0, "broadcast", "narrowcast"),
             contrast = gsub("0|1", "", contrast)) %>%
      select(contrast, sharing_type, group, estimate, p.value)
  }
  
  results %>%
    mutate(p.value = ifelse(p.value < .001, "< .001",
                      ifelse(p.value == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p.value))))) %>%
    kable(digits = 2) %>%
    kableExtra::kable_styling()
}
```

## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#bb3e03",
                      "other" = "#005f73")
palette_dv = c("self-relevance" = "#ee9b00",
               "social relevance" = "#005f73",
               "broadcast sharing" = "#5F0F40",
               "narrowcast sharing" = "#D295BF")
palette_topic = c("climate" = "#519872",
                 "health" = "#3A3357")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
data = read.csv("../data/study2_data.csv", stringsAsFactors = FALSE) %>%
  group_by(sharing_type) %>%
  mutate(msg_rel_self_z = scale(msg_rel_self, center = TRUE, scale = TRUE),
         msg_rel_social_z = scale(msg_rel_social, center = TRUE, scale = TRUE),
         msg_share_z = scale(msg_share, center = TRUE, scale = TRUE))
```

# descriptives {.tabset}
## number of articles
```{r}
data %>%
  group_by(SID) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  summarize(M = mean(n, na.rm = TRUE),
            SD = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE)) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

## percent sharing
```{r}
data %>%
  filter(sharing_type == 0) %>%
  group_by(sharing_behavior) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(total = sum(n),
         percent = (n / total) * 100) %>%
  select(-total) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

## number of shares per person
```{r}
data %>%
  filter(sharing_type == 0) %>%
  group_by(SID) %>%
  mutate(n_shares = sum(sharing_behavior, na.rm = TRUE)) %>%
  ggplot(aes(n_shares)) +
  geom_density(fill = palette_condition[1], color = NA) +
  labs(x = "\nnumber of shares per person") +
  plot_aes
```

## correlation between sharing intentions and sharing behavior {.tabset}
```{r}
data %>%
  ungroup() %>%
  select(-sharing_type) %>%
  spread(sharing_type_key, msg_share) %>%
  rmcorr::rmcorr(as.factor(SID), sharing_behavior, msg_share_narrow, data = .)
```

# H1: sharing ~ self-relvance + social relevance {.tabset}
> Greater (a) self-relevance and (b) social relevance ratings will be associated with stronger news sharing behavior.

```{r}
mod_h1_binary = glmer(sharing_behavior ~ msg_rel_self_z + msg_rel_social_z + (1 | SID),
              data = filter(data, sharing_type == 0),
              family = "binomial",
              control = glmerControl(optimizer = "bobyqa"))
```

## plot
```{r}
predicted_h1_binary = ggeffects::ggpredict(mod_h1_binary, c("msg_rel_self_z")) %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1_binary, c("msg_rel_social_z")) %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

predicted_sub_h1_binary = ggeffects::ggpredict(mod_h1_binary, terms = c("msg_rel_self_z", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h1_binary, c("msg_rel_social_z", "SID"), type = "random") %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

predicted_h1_binary %>%
  ggplot(aes(x, predicted)) +
  stat_smooth(data = predicted_sub_h1_binary, aes(group = group, color = variable),
              geom ='line', method = "lm", alpha = .1, linewidth = .75, se = FALSE) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = variable), alpha = .5, color = NA) +
  geom_line(aes(color = variable), size = 1.5) +
  facet_grid(~variable) +
  scale_color_manual(name = "", values = palette_dv) +
  scale_fill_manual(name = "", values = palette_dv) +
  labs(x = "\nrelevance rating", y = "predicted probability of sharing\n") +
  plot_aes +
    theme(legend.position = "none")
```

## model table
```{r}
table_h1_binary = table_model(mod_h1_binary, logistic = TRUE)

table_h1_binary %>%
    kable()  %>%
    kableExtra::kable_styling()
```

## summary
```{r}
summary(mod_h1_binary)
```

# H3: sharing ~ intervention condition {.tabset}
>  Compared to the control condition, the (a) self-focused and (b) other-focused conditions will increase news sharing behavior.

```{r}
mod_h3_binary = glmer(sharing_behavior ~ 1 + article_cond + (1 | SID),
              data = filter(data, sharing_type == 0),
              family = "binomial",
              control = glmerControl(optimizer = "bobyqa"))
```

## plot
```{r}
predicted_h3_binary = ggeffects::ggpredict(mod_h3_binary, c("article_cond")) %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))
  
predicted_sub_h3_binary = ggeffects::ggpredict(mod_h3_binary, terms = c("article_cond", "SID"), type = "random") %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

predicted_h3_binary %>%
  ggplot(aes(x = x, y = predicted)) +
  stat_summary(data = predicted_sub_h3_binary, aes(group = group), fun = "mean", geom = "line",
               size = .08, color = "grey50") +
  stat_summary(aes(group = group), fun = "mean", geom = "line", size = 1) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high), size = .5) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_alpha_manual(name = "", values = c(1, .5)) +
  labs(x = "", y = "predicted probability of sharing\n") +
  plot_aes
```

## model table
```{r}
table_h3_binary = table_model(mod_h3_binary, logistic = TRUE)

table_h3_binary %>%
    kable()  %>%
    kableExtra::kable_styling()
```

## summary
```{r}
summary(mod_h3_binary)
```

# combined table
```{r}
table_h1_binary %>% mutate(DV = "h1a-b: Sharing") %>%
  bind_rows(table_h3_binary %>% mutate(DV = "h3: Sharing")) %>%
  select(DV, everything()) %>%
  kable() %>%
  kable_styling()
```

# cite packages
```{r}
report::cite_packages()
```
