---
title: "Study 1 exploratory climate cause analysis"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 150, cache = FALSE)
options(scipen = 999)
set.seed(65)
```

In this report, we reproduce the exploratory Study 1 analyses examining differences in intervention effectiveness as a function of beliefs about climate change causes.

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if(!require('pacman')) {
  install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, kableExtra, lmerTest, boot, report, brms, tidybayes, ggpubr, tidyText, EMAtools, broom.mixed, devtools, emmeans)

if (!require(emo)) {
  devtools::install_github('hadley/emo')
}
```

## define functions
```{r}
# MLM results table function
table_model = function(model_data, sharing_type = FALSE, intercept = FALSE, spread = FALSE, study = TRUE) {
  
  mod = model_data %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("value"), -contains("study"), -contains("sharing_type"), -p), round, 2) %>%
    mutate(term = gsub("msg_", "", term),
           term = gsub("_", " ", term),
           term = gsub(":", " x ", term),
           term = gsub("z", "", term),
           term = gsub("topichealth", "topic (health)", term),
           term = gsub("rel self", "self-relevance", term),
           term = gsub("rel social", "social relevance", term),
           term = gsub("within", "within", term),
           term = gsub("between", "between", term),
           term = gsub("sharing type", "sharing type (narrowcast)", term),
           term = ifelse(grepl("between x ", term), "sharing type (narrowcast) x social relevance between", term),
           term = gsub("article condother", "other - control", term),
           term = gsub("article condself", "self - control", term),
           term = gsub("\\(Intercept\\)", "control", term),
           term = gsub("n c", "word count", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high))
  
  if (isTRUE(intercept)) {
    mod = mod %>%
      mutate(term = recode(term, "control" = "intercept"))
  }
  
  if (isTRUE(sharing_type) & isTRUE(study)) {
    mod = mod %>%
      mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                                   "msg_share_narrow" = "narrowcast sharing")) %>%
      select(study, sharing_type, term, `b [95% CI]`, df, t, p) %>%
      arrange(study)
    
  } else if (isTRUE(sharing_type) & isFALSE(study)) {
    mod = mod %>%
      mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                                   "msg_share_narrow" = "narrowcast sharing")) %>%
      select(sharing_type, term, `b [95% CI]`, df, t, p)
    
  } else if (isFALSE(sharing_type) & isFALSE(study)) {
    mod = mod %>%
      select(term, `b [95% CI]`, df, t, p)
    
  } else {
    
    mod = mod %>%
      select(study, term, `b [95% CI]`, df, t, p) %>%
      arrange(study)
  }
  
  if (isTRUE(spread)) {
    mod %>%
      select(-df, -t, -p) %>%
      spread(study, `b [95% CI]`) %>%
      kable() %>%
      kableExtra::kable_styling()
    
  } else {
    mod %>%
      kable() %>%
      kableExtra::kable_styling()
  }
}
```


## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#0a9396",
                      "other" = "#005f73")
palette_dv = c("self-relevance" = "#ee9b00",
               "social relevance" = "#005f73",
               "broadcast sharing" = "#5F0F40",
               "narrowcast sharing" = "#D295BF")
palette_sharing = c("broadcast sharing" = "#5F0F40",
                    "narrowcast sharing" = "#D295BF")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load & tidy data
```{r}
climate_belief = read.csv("../data/study1_climate_cause.csv", stringsAsFactors = FALSE) %>%
  filter(scale_name == "climate_change_cause") %>%
  select(SID, value) %>%
  rename("climate_change_cause" = value)

merged = read.csv("../data/study1_data.csv", stringsAsFactors = FALSE) %>%
  left_join(., climate_belief) %>%
  gather(sharing_type, msg_share, contains("share")) %>%
  group_by(sharing_type) %>%
  mutate(msg_share_z = scale(msg_share, scale = TRUE, center = TRUE),
         msg_rel_self_z = scale(msg_rel_self, scale = TRUE, center = TRUE),
         msg_rel_social_z = scale(msg_rel_social, scale = TRUE, center = TRUE)) 
```

# H3: sharing ~ intervention condition * climate cause {.tabset}
## run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_z ~ 1 + article_cond * climate_change_cause +
                         (1 | SID) +
                         (1 | article_number), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = merged  %>%
  group_by(sharing_type) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data_share = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest(cols = tidied) %>%
  filter(effect == "fixed") %>%
  ungroup()

predicted_data_share = model_lmer %>% 
  mutate(predicted = map(test, modelbased::estimate_contrasts,
                         contrast = "article_cond",
                         by = c("climate_change_cause=seq(2,5,.2)"))) %>%
  select(-data, -test) %>%
  unnest(cols = predicted) %>%
  mutate(Difference = Difference * -1,
         CI_low = CI_low * -1,
         CI_high = CI_high * -1) %>%
  filter(Level1 == "control")
```

## model summary table {.tabset}
```{r}
table_model(model_data_share, sharing_type = TRUE, study = FALSE)
```

## plot predicted
```{r}
predicted_data_share %>%
  mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                                   "msg_share_narrow" = "narrowcast sharing")) %>%
  ggplot(aes(x = climate_change_cause, y = Difference)) +
  geom_ribbon(aes(fill = Level2, ymin = CI_low, ymax = CI_high), alpha = 0.2) +
  geom_line(aes(colour = Level2), size = 2) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~sharing_type) +
  scale_color_manual(name = "", values = palette_condition) + 
  scale_fill_manual(name = "", values = palette_condition) + 
  labs(x = "\nclimate change cause\n(2 = mostly natural, 5 = entirely human)",
       y = "predicted difference\n(intervention - control in SD)\n") +
  plot_aes
```

# cite packages
```{r}
report::cite_packages()
```
