---
title: "Study 4 analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 300)
options(scipen = 999)
set.seed(65)
```

In this report, we reproduce the analyses testing between group differences in Study 4.

# prep data {.tabset}
First, we load the relevant packages, define functions and plotting aesthetics, and load and tidy the data.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, purrr, fs, knitr, lmerTest, ggeffects, parameters, kableExtra, boot, devtools, EMAtools, patchwork, install = TRUE)
```

## define functions
```{r}
# parameter estimate plotting function for purrr models
plot_model = function(model_data, palette, size = .75, facet = NULL, sharing_type = FALSE) {
  mod_renamed = model_data %>%
    mutate(term = gsub("msg_", "", term),
           term = gsub("_", " ", term),
           term = gsub(":", " x ", term),
           term = gsub(" z", "", term),
           term = gsub("rel self x topichealth", "self-relevance x\ntopic (health)", term),
           term = gsub("topichealth x rel social", "social relevance x\ntopic (health)", term),
           term = gsub("topichealth", "topic (health)", term),
           term = gsub("rel self", "self\nrelevance", term),
           term = gsub("rel social", "social\nrelevance", term),
           term = gsub(" within", "\nwithin", term),
           term = gsub(" between", "\nbetween", term),
           term = gsub("article condother", "other > control", term),
           term = gsub("article condself", "self > control", term),
           term = gsub("condition", "group", term),
           term = gsub("grouptimed", "group (timed)", term),
           term = gsub("groupuntimed", "group (untimed)", term),
           term = gsub("x topic \\(health\\)", "x\ntopic (health)", term)) 
  
  if (isTRUE(sharing_type)) {
    mod_renamed = mod_renamed %>%
      mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                               "msg_share_narrow" = "narrowcast sharing"))
  }
  
  mod = mod_renamed %>%
    ggplot(aes(x = term, y = estimate)) +
    geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = size, linewidth = size) +
    geom_hline(yintercept = 0, color = "grey50", linetype = "dotted") +
    coord_flip() +
    scale_fill_manual(name = "", values = palette) +
    scale_color_manual(name = "", values = palette) +
    labs(x = "", y = "\nstandardized  regression coefficient\n") +
    plot_aes
  
  if (!is.null(facet)) {
    mod + 
      facet_grid(~ get(facet))
  } else {
    mod
  }
}

# plot model predictions function
# parameter estimate plotting function for purrr models
plot_predicted = function(predicted_data, palette, size = .75, facet = NULL, sharing_type = FALSE) {

  if (isTRUE(sharing_type)) {
    predicted_data = predicted_data %>%
      mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                               "msg_share_narrow" = "narrowcast sharing"))
  }
  
  mod = predicted_data %>%
    ggplot(aes(x = group, y = predicted)) +
    geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = size, linewidth = size) +
    geom_hline(yintercept = 0, color = "grey50", linetype = "dotted") +
    coord_flip() +
    scale_fill_manual(name = "", values = palette) +
    scale_color_manual(name = "", values = palette) +
    labs(x = "", y = "\nstandardized  regression coefficient\n") +
    plot_aes
  
  if (!is.null(facet)) {
    mod + 
      facet_grid(facet)
  } else {
    mod
  }
}


# MLM results table function
table_model = function(model_data, sharing_type = FALSE, intercept = FALSE, spread = FALSE) {
  
  mod = model_data %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("value"), -contains("sharing_type"), -p), round, 2) %>%
    mutate(term = gsub("msg_", "", term),
           term = gsub("_", " ", term),
           term = gsub(":", " x ", term),
           term = gsub("z", "", term),
           term = gsub("topichealth", "topic (health)", term),
           term = gsub("rel self", "self-relevance", term),
           term = gsub("rel social", "social relevance", term),
           term = gsub("within", "within", term),
           term = gsub("between", "between", term),
           term = gsub("sharing type", "sharing type (narrowcast)", term),
           term = ifelse(grepl("between x ", term), "sharing type (narrowcast) x social relevance between", term),
           term = gsub("article condself", "self - control", term),
           term = gsub("article condother", "other - control", term),
           term = gsub("conditiontimed", "group (timed)", term),
           term = gsub("conditionuntimed", "group (untimed)", term),
           term = gsub("\\(Intercept\\)", "control", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high))
  
  if (isTRUE(intercept)) {
    mod = mod %>%
      mutate(term = recode(term, "control" = "intercept"))
  }
  
    if (isTRUE(sharing_type)) {
    mod = mod %>%
      mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                               "msg_share_narrow" = "narrowcast sharing")) %>%
      select(sharing_type, term, `b [95% CI]`, df, t, p)
      
    } else {
      
    mod = mod %>%
      select(term, `b [95% CI]`, df, t, p)
    }
  
  if (isTRUE(spread)) {
    mod %>%
      select(-df, -t, -p) %>%
      spread(`b [95% CI]`) %>%
      kable() %>%
      kableExtra::kable_styling()
    
  } else {
    mod %>%
      kable() %>%
      kableExtra::kable_styling()
  }
}
```

## define aesthetics
```{r}
palette_condition = c("self" = "#ee9b00",
                      "control" = "#bb3e03",
                      "other" = "#005f73")
palette_group = c("comment" = "#005f73",
                  "timed" = "#5F0F40",
                  "untimed" = "#D295BF")
palette_group_con = c("timed > comment" = "#5F0F40",
                      "untimed > comment" = "#D295BF")


plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
data = read.csv("../data/study4_data.csv", stringsAsFactors = FALSE) %>%
  select(-sharing_type) %>%
  rename("sharing_type" = sharing_type_key) %>%
  group_by(sharing_type) %>%
  mutate(article_cond = ifelse(article_cond == "social", "other", article_cond),
         msg_share_z = scale(msg_share, center = TRUE, scale = TRUE),
         msg_rel_self_z = scale(msg_rel_self, center = TRUE, scale = TRUE),
         msg_rel_social_z = scale(msg_rel_social, center = TRUE, scale = TRUE)) %>%
  rename("condition" = group) %>%
  ungroup()

sub_conditions = data %>%
  select(SID, condition) %>%
  unique()
```

# descriptives {.tabset}
## group ns
Sample size by group

```{r}
data %>%
  select(condition, SID) %>%
  unique() %>%
  group_by(condition) %>%
  summarize(n = n()) %>%
  kable() %>%
  kable_styling()
```

## ratings
Summarize means and SDs
```{r}
data %>%
  select(-msg_share_z) %>%
  spread(sharing_type, msg_share) %>%
  gather(variable, value, msg_share_broad, msg_share_narrow, msg_rel_self, msg_rel_social) %>%
  group_by(variable) %>%
  summarize(M = mean(value, na.rm = TRUE),
            SD = sd(value, na.rm = TRUE)) %>%
  mutate(variable = recode(variable, "msg_rel_self" ="self-relevance",
                           "msg_rel_social" = "social relevance",
                           "msg_share_broad" = "broadcast intention",
                           "msg_share_narrow" = "narrowcast intention")) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

# H1: sharing ~ self-relvance + social relevance {.tabset}
> Greater (a) self-relevance and (b) social relevance ratings will be associated with stronger news sharing intentions and behavior.

## run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_z ~ 1 + msg_rel_self_z * condition + msg_rel_social_z * condition +
                         (1 + msg_rel_self_z + msg_rel_social_z | SID) +
                         (1 | article_number), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}
model_lmer = data  %>%
  group_by(sharing_type) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest(cols = tidied) %>%
  filter(effect == "fixed") %>%
  ungroup()

predicted_data = model_lmer %>% 
  mutate(`self-relevance` = map(test, ggeffects::ggpredict,
                                terms = c("msg_rel_self_z [-3,-2,-1,0,1,2,3]", "condition")),
         `social relevance` = map(test, ggeffects::ggpredict,
                                  terms = c("msg_rel_social_z [-3,-2,-1,0,1,2,3]", "condition"))) %>%
  select(-data, -test) %>%
  gather(variable, predicted, contains("relevance")) %>%
  unnest(cols = predicted) %>%
  mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                               "msg_share_narrow" = "narrowcast sharing"))

predicted_random_data = model_lmer %>% 
  mutate(`self-relevance` = map(test, ggeffects::ggpredict,
                                terms = c("msg_rel_self_z [-3,-2,-1,0,1,2,3]", "condition", "SID"), type = "random"),
         `social relevance` = map(test, ggeffects::ggpredict,
                                  terms = c("msg_rel_social_z [-3,-2,-1,0,1,2,3]", "condition", "SID"), type = "random")) %>%
  select(-data, -test) %>%
  gather(variable, predicted, contains("relevance")) %>%
  unnest(cols = predicted) %>%
  mutate(sharing_type = recode(sharing_type, "msg_share_broad" = "broadcast sharing",
                               "msg_share_narrow" = "narrowcast sharing"))
```

## model summary table {.tabset}
```{r}
table_model(model_data, sharing_type = TRUE, intercept = TRUE)
```

## plot continuous relationships
```{r, fig.width=8, fig.height=9}
(plot_a = predicted_data %>%
  ggplot(aes(x, predicted)) +
  stat_smooth(data = predicted_random_data, aes(group = interaction(facet, group), color = group),
              geom = "line", method = "lm", alpha = .15, linewidth = .1, se = FALSE) +
  geom_ribbon(aes(fill = group, ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = group), size = 1) + 
  facet_grid(variable ~ sharing_type) +
  scale_fill_manual(name = "", values = palette_group) +
  scale_color_manual(name = "", values = palette_group) +
  #coord_cartesian(ylim = c(-2, 2.5)) +
  labs(x = "\nrelevance rating (SD)", y = "predicted sharing intention (SD)\n") + 
  plot_aes)
```

## plot coefficients
```{r, fig.width=12, fig.height=7}
plot_model(model_data, palette, facet = "sharing_type", sharing_type = TRUE, size = 1)
```

# H2: relevance ~ intervention condition {.tabset}
> Compared to the control condition, the (a) self-focused condition will increase self-relevance ratings, and (b) other-focused condition will increase social relevance ratings.

## H2a self-relevance {.tabset}
### run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_rel_self_z ~ 1 + article_cond * condition +
                         (1 | SID) +
                         (1 | article_number), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = data  %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data_self = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest(cols = tidied) %>%
  filter(effect == "fixed") %>%
  ungroup()

predicted_data_self = model_lmer %>% 
  mutate(predicted = map(test, ggeffects::ggpredict, terms = c("article_cond", "condition"))) %>%
  select(-data, -test) %>%
  unnest(cols = predicted)
```

### model summary table {.tabset}
```{r}
table_model(model_data_self)
```

### plot coefficients
```{r, fig.width=12, fig.height=4}
plot_predicted(predicted_data_self, facet = "~ x", palette, size = 1)
```

## H2b social relevance {.tabset}
### run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_rel_social_z ~ 1 + article_cond * condition +
                         (1 | SID) +
                         (1 | article_number), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = data  %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data_social = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest(cols = tidied) %>%
  filter(effect == "fixed") %>%
  ungroup()

predicted_data_social = model_lmer %>% 
  mutate(predicted = map(test, ggeffects::ggpredict, terms = c("article_cond", "condition"))) %>%
  select(-data, -test) %>%
  unnest(cols = predicted)
```

### model summary table {.tabset}
```{r}
table_model(model_data_social)
```

### plot coefficients
```{r, fig.width=12, fig.height=4}
plot_predicted(predicted_data_social, facet = "~ x", palette, size = 1)
```

# H3: sharing ~ intervention condition {.tabset}
> Compared to the control condition, the (a) self-focused and (b) other-focused conditions will increase news sharing intentions and behavior.

## run models
```{r, fig.width=6, fig.height=6}
fit_mod = function(data){
  mod = lmerTest::lmer(msg_share_z ~ 1 + article_cond * condition +
                         (1 | SID) +
                         (1 | article_number), data = data,
                       control = lmerControl(optimizer = "bobyqa"))
  return(mod)
}

model_lmer = data  %>%
  group_by(sharing_type) %>%
  nest() %>%
  mutate(test = map(data, fit_mod))

model_data_share = model_lmer %>% 
  mutate(tidied = map(test, broom.mixed::tidy, conf.int = TRUE)) %>%
  select(-data, -test) %>%
  unnest(cols = tidied) %>%
  filter(effect == "fixed") %>%
  ungroup()

predicted_data_share = model_lmer %>% 
  mutate(predicted = map(test, ggeffects::ggpredict, terms = c("article_cond", "condition"))) %>%
  select(-data, -test) %>%
  unnest(cols = predicted)
```

## model summary table {.tabset}
```{r}
table_model(model_data_share, sharing_type = TRUE)
```

## plot coefficients
```{r, fig.width=10, fig.height=9}
plot_predicted(predicted_data_share, facet = "x ~ sharing_type", palette, size = 1, sharing_type = TRUE)
```

## plot contrasts
```{r, fig.width=8, fig.height=8}
(plot_b = model_data_share %>%
  mutate(model = recode(sharing_type, "msg_share_broad" = "broadcast\nsharing",
                        "msg_share_narrow" = "narrowcast\nsharing")) %>%
  bind_rows(model_data_self %>% mutate(model = "self\nrelevance")) %>%
  bind_rows(model_data_social %>% mutate(model = "social\nrelevance")) %>%
  filter(!term == "(Intercept)") %>%
  mutate(term = recode(term, "article_condother" = "other > control",
                       "article_condself" = "self > control",
                       "article_condother:conditiontimed" = "other > control x group (timed > comment)",
                       "article_condself:conditiontimed" = "self > control x group (timed > comment)",
                       "article_condother:conditionuntimed" = "other > control x group (untimed > comment)",
                       "article_condself:conditionuntimed" = "self > control x group (untimed > comment)",                      
                       "conditiontimed" = "group (timed > comment)",
                       "conditionuntimed" = "group (untimed > comment)")) %>%
  filter(grepl("x", term)) %>%
  extract(term, c("term", "group"), "(.*) x group \\((.*)\\)") %>%
  mutate(term = factor(term, levels = c("self > control", "other > control"))) %>%
  ggplot(aes(x = model, y = estimate, color = group)) +
    geom_pointrange(aes( ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1, linewidth = 1) +
    geom_hline(yintercept = 0, color = "grey50", linetype = "dotted") +
    coord_flip() +
    facet_grid(~ term) +
    scale_fill_manual(name = "", values = palette_group_con) +
    scale_color_manual(name = "", values = palette_group_con) +
    labs(x = "", y = "\nstandardized  regression coefficient\n") +
    plot_aes)

```


# combined H1-3 coefficient plot
```{r, fig.width=22, fig.height=10, warning=FALSE}
(plot_a + labs(title = "H1: Correlational relationships") + plot_b + labs(title = "H2-3: Intervention effects")) +
  patchwork::plot_layout(ncol = 2) & theme(legend.position = 'top') & patchwork::plot_annotation(tag_levels = 'A')
```

# cite packages
```{r}
report::cite_packages()
```
