---
title: "Follow-up behavioral study analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dpi = 300)
options(scipen = 999)
set.seed(65)
```

# define functions
```{r}
# MLM results table function
table_model = function(model_data, eff_size = TRUE, word_count = TRUE) {
  
  results = model_data %>%
    broom.mixed::tidy(conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    select(-group, -effect) %>%
    mutate_at(vars(-contains("term"), -contains("p")), round, 2) %>%
    mutate(term = gsub("article_cond", "", term),
           term = gsub("\\(Intercept\\)", "control", term),
           term = gsub("sharing_type", "sharing type", term),
           term = gsub("msg_rel_self_between", "self-relevance", term),
           term = gsub("msg_rel_social_between", "social relevance", term),
           term = gsub("grouptimed", "group (timed)", term),
           term = gsub("groupuntimed", "group (untimed)", term),
           term = gsub("contentclimate", "content (climate)", term),
           term = gsub("siteUSA", "sample (USA)", term),
           term = gsub("n_c", "word count", term),
           term = gsub(":", " x ", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high)) 
  
  if (word_count == TRUE) {
    results = results %>%
      mutate(term = gsub("control", "intercept", term))
  }
  
  if (eff_size == TRUE) {
    eff_size = lme.dscore(model_data, data = data, type = "lme4") %>%
      rownames_to_column(var = "term") %>%
      mutate(term = gsub("article_cond", "", term),
             term = gsub("article_cond", "", term),
             term = gsub("\\(Intercept\\)", "control", term),
             term = gsub("sharing_type", "sharing type", term),
             term = gsub("msg_rel_self_between", "self-relevance", term),
             term = gsub("msg_rel_social_between", "social relevance", term),
             term = gsub("contentclimate", "content (climate)", term),
             term = gsub(":", " x ", term),
             d = sprintf("%.2f", d)) %>%
      select(term, d)
    
    results %>%
      left_join(., eff_size) %>%
      mutate(d = ifelse(is.na(d), "--", d)) %>%
      select(term, `b [95% CI]`, d, df, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
    
  } else {
    results %>%
      select(term, `b [95% CI]`, df, t, p) %>%
      kable() %>%
      kableExtra::kable_styling()
  }
}

# simple effects function
simple_effects = function(model, sharing = FALSE) {
  if(sharing == FALSE) {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("control", contrast)) %>%
      select(contrast, group, estimate, p.value)
  } else {
    results = emmeans::contrast(emmeans::emmeans(model, ~ article_cond | group + sharing_type),
                            "revpairwise", by = "group", adjust = "none") %>%
      data.frame() %>%
      filter(grepl("- control", contrast)) %>%
      filter(!grepl("^control", contrast)) %>%
      extract(contrast, c("exp_sharing", "control_sharing"), ".* (0|1) - control (0|1)", remove = FALSE) %>%
      filter(exp_sharing == control_sharing) %>%
      mutate(sharing_type = ifelse(exp_sharing == 0, "broadcast", "narrowcast"),
             contrast = gsub("0|1", "", contrast)) %>%
      select(contrast, sharing_type, group, estimate, p.value)
  }
  
  results %>%
    mutate(p.value = ifelse(p.value < .001, "< .001",
                      ifelse(p.value == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p.value))))) %>%
    kable(digits = 2) %>%
    kableExtra::kable_styling()
}
```

# prep data {.tabset}
First, we load the relevant packages and data, and define the plotting aesthetics.

## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, kableExtra, lmerTest, boot, report, brms, tidybayes, ggpubr, EMAtools, broom.mixed)
```

## define aesthetics
```{r}
palette_condition = c("#ee9b00", "#bb3e03", "#005f73")
palette_dv = c("#ee9b00", "#005f73", "#56282D")
palette_sharing = c("#0a9396", "#ee9b00")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load data
```{r}
data = read.csv("../data/study2_data.csv", stringsAsFactors = FALSE) %>%
  mutate(article_cond = ifelse(article_cond == "social", "other", article_cond))

n_words = read.csv("../data/study2_n_words.csv", stringsAsFactors = FALSE) %>%
  mutate(article_cond = ifelse(article_cond == "social", "other", article_cond))
```

# group ns
Not sure whey we ended up with fewer people in the comment condition. Let's look into that.

```{r}
data %>%
  select(group, SID) %>%
  unique() %>%
  group_by(group) %>%
  summarize(n = n()) %>%
  kable() %>%
  kable_styling()
```

# manipulation checks {.tabset}
## self-relevance {.tabset}
Test whether messages in the self condition will be rated as more self-relevant than messages in the control condition as a function of group.

**Results**

`r emo::ji("check")` We replicate our previous work in the comment group: the self condition increases self-relevance compared to the control

`r emo::ji("check")` This effect is smaller for both the timed and untimed groups

```{r}
mod_h1 = lmer(msg_rel_self ~ 1 + article_cond * group + (1 + article_cond | SID),
              data = filter(data, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))
```

### model summary table
```{r}
table_model(mod_h1, eff_size = FALSE)
```

### simple effects by group
```{r}
simple_effects(mod_h1)
```

## social relevance {.tabset}
Test whether messages in the social condition will be rated as more socially relevant than messages in the control condition as a function of group.

**Results**

`r emo::ji("check")` We replicate our previous work in the comment group: the social condition increases social relevance compared to the control

`r emo::ji("check")` This effect is smaller for both the timed and untimed groups

```{r}
mod_h2 = lmer(msg_rel_social ~ 1 + article_cond * group + (1 + article_cond | SID),
              data = filter(data, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))
```

### model summary table
```{r}
table_model(mod_h2, eff_size = FALSE)
```

### simple effects by group
```{r}
simple_effects(mod_h2)
```

## plot predicted effects
```{r, fig.width=5, fig.height=4.5}
# generate predicted values
predicted_h1 = ggeffects::ggpredict(mod_h1, c("article_cond", "group")) %>%
              data.frame() %>%
  mutate(model = "self-relevance")

predicted_h2 = ggeffects::ggpredict(mod_h2, c("article_cond", "group")) %>%
              data.frame() %>%
  mutate(model = "social relevance")

# manipulation check plot
bind_rows(predicted_h1, predicted_h2) %>%
  mutate(x = factor(x, levels = c("self", "control", "other"))) %>%
  ggplot(aes(x = group, y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1) +
  facet_grid(~ model) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition) +
  labs(x = "", y = "\nmean predicted relevance rating") +
  plot_aes +
  theme(legend.position = "top")
```

# condition effects narrowcasting only {.tabset}
Test whether messages in the experimental conditions will evoke higher sharing intentions than messages in the control condition, and whether this is moderated by sharing type as a function group.

**Results**

`r emo::ji("check")` We replicate our previous work in the comment group: the self and social conditions increase sharing intentions compared to the control, and these effects are stronger for narrowcast compared to broadcasting sharing intentions

`r emo::ji("check")` These effects were smaller for both the timed and untimed groups

```{r}
mod_h3 = lmer(msg_share ~ 1 + article_cond*group + (1 + article_cond | SID),
              data = filter(data, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))
```


## plot predicted effects
```{r, fig.width=5, fig.height=4.5}
# generate predicted values
predicted_h3 = ggeffects::ggpredict(mod_h3, c("article_cond", "group")) %>%
              data.frame() %>%
  mutate(model = "sharing")

# causal analysis plot
predicted_h3 %>%
  mutate(x = factor(x, levels = c("self", "control", "other"))) %>%
  ggplot(aes(x = group, y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition) +
  labs(x = "", y = "\nmean predicted sharing intention rating") +
  plot_aes +
  theme(legend.position = "top")
```

## model summary table
```{r}
table_model(mod_h3, eff_size = FALSE)
```

## simple effects by group
```{r}
simple_effects(mod_h3, sharing = FALSE)
```

# combined plot
```{r, fig.width=8, fig.height=5.75}
bind_rows(predicted_h1, predicted_h2, predicted_h3) %>%
  mutate(model = factor(model, levels = c("self-relevance", "social relevance", "sharing")),
         x = factor(x, levels = c("self", "control", "other")),
         group = ifelse(group == "timed", "reflect:\ntimed",
                 ifelse(group == "untimed", "reflect:\nuntimed", "comment")),
         group = factor(group, levels = c("reflect:\ntimed", "reflect:\nuntimed", "comment"))) %>%
  ggplot(aes(x = group, y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1.5) +
  facet_grid(~ model) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition) +
  labs(x = "", y = "\npredicted rating") +
  plot_aes +
  theme(legend.position = "top")
```

# condition effects by sharing type {.tabset}
Test whether messages in the experimental conditions will evoke higher sharing intentions than messages in the control condition, and whether this is moderated by sharing type as a function group.

**Results**

`r emo::ji("check")` We replicate our previous work in the comment group: the self and social conditions increase sharing intentions compared to the control, and these effects are stronger for narrowcast compared to broadcasting sharing intentions

`r emo::ji("check")` These effects were smaller for both the timed and untimed groups

```{r}
mod_h3_h4 = lmer(msg_share ~ 1 + article_cond*sharing_type*group + (1 + sharing_type | SID),
              data = data,
              control = lmerControl(optimizer = "bobyqa"))
```


## plot predicted effects
```{r, fig.width=7, fig.height=5}
# generate predicted values
predicted_h3_h4 = ggeffects::ggpredict(mod_h3_h4, c("article_cond", "sharing_type", "group")) %>%
              data.frame() %>%
  mutate(group = ifelse(group == "0", "broadcast sharing", "narrowcast sharing"),
         facet = ifelse(grepl("time", facet), sprintf("reflect:\n%s", facet), "comment"),
         facet = factor(facet, levels = c("reflect:\ntimed", "reflect:\nuntimed", "comment")))

# causal analysis plot
predicted_h3_h4 %>%
  mutate(group = gsub(" sharing", "", group)) %>%
  ggplot(aes(x = facet, y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1) +
  facet_grid(~ group) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition) +
  labs(x = "", y = "\nmean predicted sharing intention rating") +
  plot_aes +
  theme(legend.position = "top")
```

## model summary table
```{r}
table_model(mod_h3_h4, eff_size = FALSE)
```

## simple effects by group
```{r}
simple_effects(mod_h3_h4, sharing = TRUE)
```



# word count analyses {.tabset}
Test whether word count is higher in the experimental conditions, and whether it is positively associated with self and social relevance, and sharing intention ratings.

## summarize
```{r}
words_ratings = n_words %>%
  left_join(., data) %>%
  ungroup() %>%
  mutate(n_c = n - mean(n, na.rm = TRUE))

n_words %>%
  group_by(article_cond) %>%
  summarize(mean = mean(n, na.rm = TRUE),
            sd = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE)) %>%
  kable(digits = 2) %>%
  kableExtra::kable_styling()
```

## condition model {.tabset}

Is word count higher in the experimental conditions compared to the control condition?

**Results**

`r emo::ji("check")` The word count is higher in the experimental conditions compared to the control condition

```{r}
mod_words = lmer(n ~ 1 + article_cond + (1 + article_cond | SID),
              data = n_words,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot predicted effects
```{r}
predicted = ggeffects::ggpredict(mod_words, c("article_cond")) %>%
              data.frame()

predicted %>%
  ggplot(aes(x = "", y = predicted, color = x)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(.5), size = 1) +
  coord_flip() +
  scale_color_manual(name = "", values = palette_condition) +
  labs(x = "", y = "\nmean predicted word count") +
  plot_aes +
  theme(legend.position = "top")
```

### model summary
```{r}
table_model(mod_words, eff_size = FALSE)
```

## relevance models {.tabset}
Is word count positively associated with self and social relevance ratings?

### self-relevance {.tabset}

**Results**

`r emo::ji("check")` Word count is positively associated with self-relevance ratings

```{r}
mod_words_h1 = lmer(msg_rel_self ~ 1 + n_c + (1 + n_c | SID),
              data = filter(words_ratings, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))
```

#### plot predicted effects
```{r}
values = seq(-15, 60, 10)
predicted_self = ggeffects::ggpredict(mod_words_h1, terms = "n_c [values]") %>%
  data.frame()

predicted_self %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25) +
  geom_line(size = 1) +
  coord_cartesian(ylim = c(40, 110)) +
  labs(x = "\nword count (grand mean-centered)", y = "predicted self-relevance rating\n") +
  plot_aes
```

#### model summary
```{r}
table_model(mod_words_h1, eff_size = FALSE, word_count = TRUE)
```

### social relevance {.tabset}

**Results**

`r emo::ji("check")` Word count is positively associated with social relevance ratings


```{r}
mod_words_h2 = lmer(msg_rel_social ~ 1 + n_c + (1 + n_c | SID),
              data = filter(words_ratings, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))

```

#### plot predicted effects
```{r}
values = seq(-15, 60, 10)
predicted_social = ggeffects::ggpredict(mod_words_h2, terms = "n_c [values]") %>%
  data.frame()

predicted_social %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25) +
  geom_line(size = 1) +
  coord_cartesian(ylim = c(40, 105)) +
  labs(x = "\nword count (grand mean-centered)", y = "predicted social relevance rating\n") +
  plot_aes
```

#### model summary
```{r}
table_model(mod_words_h2, eff_size = FALSE, word_count = TRUE)
```

### combined plot
```{r, fig.width=6, fig.height=5}
data_raw = words_ratings %>%
  filter(sharing_type == 1) %>%
  select(SID, n_c, msg_rel_self, msg_rel_social) %>%
  gather(group, predicted, contains("msg")) %>%
  rename("x" = n_c) %>%
  mutate(group = ifelse(group == "msg_rel_self", "self","social"),
         group = factor(group, levels = c("self", "social")))
  
predicted_self %>%
  mutate(group = "self") %>%
  bind_rows(., predicted_social %>%  mutate(group = "social")) %>%
  mutate(group = factor(group, levels = c("self", "social"))) %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  geom_point(data = data_raw, aes(x, predicted, color = group, fill = group), alpha = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25, color = NA) +
  geom_line(size = 2) +
  scale_x_continuous(breaks = seq(-10, 60, 10)) +
  scale_y_continuous(breaks = seq(0, 100, 25)) +
  scale_color_manual(values = c(palette_condition[1], palette_condition[3]), name = "") + 
  scale_fill_manual(values = c(palette_condition[1], palette_condition[3]), name = "") + 
  labs(x = "\nword count (grand mean-centered)", y = "predicted relevance rating\n") +
  plot_aes +
  theme(legend.position = c(.85, .21))
```

## sharing models {.tabset}
Is word count positively associated with sharing intention ratings?

**Results**

`r emo::ji("check")` Word count is positively associated with sharing intentions (averaging across sharing types), but doesn't differ by sharing type

```{r}
mod_words_h3 = lmer(msg_share ~ 1 + n_c + (1 + n_c | SID),
              data = filter(words_ratings, sharing_type == 1),
              control = lmerControl(optimizer = "bobyqa"))
```

### plot predicted effects
```{r}
values = seq(-15, 60, 10)
predicted_sharing = ggeffects::ggpredict(mod_words_h3, terms = c("n_c [values]")) %>%
  data.frame()

predicted_sharing %>%
  ggplot(aes(x, predicted)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25, color = NA) +
  geom_line(size = 1) +
  scale_color_manual(values = palette_sharing, name = "") +
  scale_fill_manual(values = palette_sharing, name = "") +
  labs(x = "\nword count (grand mean-centered)", y = "predicted sharing intention rating\n") +
  plot_aes
```

### model summary
```{r}
table_model(mod_words_h3, eff_size = FALSE, word_count = TRUE)
```

### combined plot
```{r}
data_raw = words_ratings %>%
  filter(sharing_type == 1) %>%
  select(SID, n_c, msg_rel_self, msg_rel_social, msg_share) %>%
  gather(group, predicted, contains("msg")) %>%
  rename("x" = n_c) %>%
  mutate(group = ifelse(group == "msg_rel_self", "self-relevance",
                 ifelse(group == "msg_rel_social", "social relevance", "sharing")),
         group = factor(group, levels = c("self-relevance", "social relevance", "sharing")))
  
predicted_self %>%
  mutate(group = "self-relevance") %>%
  bind_rows(., predicted_social %>%  mutate(group = "social relevance")) %>%
  bind_rows(., predicted_sharing %>%  mutate(group = "sharing")) %>%
  mutate(group = factor(group, levels = c("self-relevance", "social relevance", "sharing"))) %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  geom_point(data = data_raw, aes(x, predicted, color = group, fill = group), alpha = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25, color = NA) +
  geom_line(size = 2) +
  scale_x_continuous(breaks = seq(-10, 60, 10)) +
  scale_y_continuous(breaks = seq(0, 100, 25)) +
  scale_color_manual(values = palette_dv, name = "") + 
  scale_fill_manual(values = palette_dv, name = "") + 
  labs(x = "\nword count (grand mean-centered)", y = "predicted rating\n") +
  plot_aes +
  theme(legend.position = c(.85, .21))
```

## sharing models by sharing type {.tabset}
Is word count positively associated with sharing intention ratings?

**Results**

`r emo::ji("check")` Word count is positively associated with sharing intentions (averaging across sharing types), but doesn't differ by sharing type

```{r}
mod_words_h3 = lmer(msg_share ~ 1 + n_c * sharing_type + (1 + n_c | SID),
              data = words_ratings,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot predicted effects
```{r}
values = seq(-20, 60, 10)
predicted = ggeffects::ggpredict(mod_words_h3, terms = c("n_c [values]", "sharing_type")) %>%
  data.frame() %>%
  mutate(group = ifelse(group == "0", "broadcast sharing", "narrowcast sharing"))

predicted %>%
  ggplot(aes(x, predicted, color = group, fill = group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .25, color = NA) +
  geom_line(size = 1) +
  scale_color_manual(values = palette_sharing, name = "") +
  scale_fill_manual(values = palette_sharing, name = "") +
  labs(x = "\nword count (grand mean-centered)", y = "predicted sharing intention rating\n") +
  plot_aes
```

### model summary
```{r}
table_model(mod_words_h3, eff_size = FALSE, word_count = TRUE)
```

# moderation by article topic comment group only {.tabset}

These analyses explore whether the analyses reported in study 2 of the main manuscript are moderated by article topic (health or climate).

```{r}
data_comment = data %>%
  filter(group == "comment") %>%
  select(-group)
```


## H2 {.tabset}
> Are the effects of the experimental manipulations on relevance moderated by article topic?

### self-relevance {.tabset}
There is a main effect of topic such that health articles are rated as more self-relevant than climate articles.

The was also an interaction such that the effect of the self-focused condition on self-relevance was weaker for health articles.

```{r}
mod_h2a = lmer(msg_rel_self ~ article_cond * topic + (1 | SID),
               data = filter(data_comment, sharing_type == 0), 
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2a = table_model(mod_h2a)

table_h2a
```

#### summary
```{r}
summary(mod_h2a)
```

### social relevance {.tabset}

There is a main effect of topic such that health articles are rated as more socially relevant than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h2b = lmer(msg_rel_social ~ article_cond * topic + (1 | SID),
               data = filter(data_comment, sharing_type == 0), 
              control = lmerControl(optimizer = "bobyqa"))
```

#### model table
```{r}
table_h2b = table_model(mod_h2b)

table_h2b
```

#### summary
```{r}
summary(mod_h2b)
```

### combined plot
```{r}
predicted_h2 = ggeffects::ggpredict(mod_h2a, c("article_cond", "topic")) %>%
  data.frame() %>%
  mutate(model = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h2b, c("article_cond", "topic")) %>%
              data.frame() %>%
              mutate(model = "social relevance")) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

ind_data_h2 = data_comment %>%
  rename("x" = article_cond,
         "group" = topic) %>%
  gather(model, predicted, msg_rel_self, msg_rel_social) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")),
         model = gsub("msg_rel_self", "self-relevance", model),
         model = gsub("msg_rel_social", "social relevance", model))
  
(plot_h2 = predicted_h2 %>%
  ggplot(aes(x = x, y = predicted)) +
  # stat_summary(data = ind_data_h2, aes(group = SID, linetype = group), fun = "mean", geom = "line",
  #              size = .1, color = "grey50") +
  stat_summary(aes(group = group, linetype = group),
               fun = "mean", geom = "line", size = 1, position = position_dodge(.1)) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high, group = group),
                  size = .75, position = position_dodge(.1)) +
  facet_grid(~model) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_linetype_manual(name = "", values = c("solid", "dotted")) +
  labs(x = "", y = "predicted rating\n") +
  plot_aes +
  theme(legend.position = c(.85, .15)))
```

## H3 {.tabset}

> Are the relationships between self and social relevance and sharing intentions moderated by article topic?

The relationship between self-relevance and sharing intentions was not moderated by topic.

However, the relationship between social relevance and sharing intentions was slightly stronger for health articles compared to climate articles.

```{r}
mod_h3 = lmer(msg_share ~ msg_rel_self * topic + msg_rel_social * topic + (1 + msg_rel_self | SID),
              data = data_comment,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted = ggeffects::ggpredict(mod_h3, c("msg_rel_self", "topic")) %>%
  data.frame() %>%
  mutate(variable = "self-relevance") %>%
  bind_rows(ggeffects::ggpredict(mod_h3, c("msg_rel_social", "topic")) %>%
              data.frame() %>%
              mutate(variable = "social relevance"))

points = data_comment %>%
  rename("predicted" = msg_share,
         "group" = topic) %>%
  gather(variable, x, msg_rel_self, msg_rel_social) %>%
  mutate(variable = gsub("msg_rel_self", "self-relevance", variable),
         variable = gsub("msg_rel_social", "social relevance", variable))

(plot_rel_sharing = predicted %>%
  ggplot(aes(x, predicted)) +
  geom_point(data = points, aes(x, predicted, color = group),
             alpha = .5, size = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = group), alpha = .2, color = NA) +
  geom_line(aes(color = group), size = 1) +
  facet_grid(~variable) +
  # scale_color_manual(name = "", values = palette_topic) +
  # scale_fill_manual(name = "", values = palette_topic) +
  labs(x = "\nrating", y = "predicted sharing intention\n") +
  plot_aes)
```

### model table
```{r}
table_h3 = table_model(mod_h3)

table_h3
```

### summary
```{r}
summary(mod_h3)
```

## H5 {.tabset}
> Are the effect of the experimental manipulations on sharing intentions moderated by article topic?

There is a main effect of topic, such that health articles have higher sharing intentions than climate articles.

These data are not consistent with moderation by topic.

```{r}
mod_h5 = lmer(msg_share ~ article_cond * topic + (1 | SID),
              data = data_comment,
              control = lmerControl(optimizer = "bobyqa"))
```

### plot
```{r}
predicted_h5 = ggeffects::ggpredict(mod_h5, c("article_cond", "topic")) %>%
  data.frame() %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))

ind_data_h5 = data_comment %>%
  rename("x" = article_cond,
         "predicted" = msg_share,
         "group" = topic) %>%
  mutate(x = factor(x, levels = c("self", "control", "other")))
  
predicted_h5 %>%
  ggplot(aes(x = x, y = predicted)) +
  # stat_summary(data = ind_data_h5, aes(group = SID, linetype = group),
  #              fun = "mean", geom = "line", size = .25, color = "grey50") +
  stat_summary(aes(group = group, linetype = group),
               fun = "mean", geom = "line", size = 1.5) +
  geom_pointrange(aes(color = x, ymin = conf.low, ymax = conf.high, group = group),
                  size = 1.5) +
  scale_color_manual(name = "", values = palette_condition, guide = "none") +
  scale_linetype_manual(name = "", values = c("solid", "dotted")) +
  labs(x = "", y = "predicted sharing intention\n") +
  plot_aes +
  theme(legend.position = c(.85, .15))
 
```

### model table
```{r}
table_h5 = table_model(mod_h5)

table_h5
```

### summary
```{r}
summary(mod_h5)
```

## combined table
```{r}
# table_h1a %>% mutate(DV = "H1a: Self-relevance") %>%
#   bind_rows(table_h1b %>% mutate(DV = "H1b: Social relevance")) %>%
#   bind_rows(table_h2a %>% mutate(DV = "H2a: Self-relevance")) %>%
#   bind_rows(table_h2b %>% mutate(DV = "H2b: Social relevance")) %>%
#   bind_rows(table_h3 %>% mutate(DV = "H3a-b: Sharing intention")) %>%
#   bind_rows(table_h4a %>% mutate(DV = "H4a: Self-referential ROI")) %>%
#   bind_rows(table_h4b %>% mutate(DV = "H4b: Mentalizing ROI")) %>%
#   bind_rows(table_h5 %>% mutate(DV = "H5: Sharing intention")) %>%
#   bind_rows(table_h6a %>% mutate(DV = "H6a: Sharing intention")) %>%
#   bind_rows(table_h6b %>% mutate(DV = "H6b: Sharing intention")) %>%
#   select(DV, everything()) %>%
#   kable() %>%
#   kable_styling()
```
